---
title: "Digital Marketing Campaign Analytics"
subtitle: "Group Project Final Report Presentation"
author:
  - "Member 1 Name"
  - "Member 2 Name"
  - "Grace Sen"
  - "Sandy Zhu"
  - "Jungmin Woo"
date: today
format:
  revealjs:
    theme: simple
    slide-number: c/t
    footer: "Digital Marketing Campaign Analytics"
    transition: fade
    embed-resources: false
    code-fold: true
    code-tools: true
    scrollable: true
    toc: false
    chalkboard: true
execute:
  echo: true
  warning: false
  message: false
---

## Cover Slide {background-color="#1f3864"}

::: {style="text-align: center; margin-top: 15%; color: white;"}
# Digital Marketing Campaign Analytics
### Predicting Customer Conversion, Engagement, and ROI


`r format(Sys.Date(), "%B %d, %Y")`
:::

## Table of Contents

::: incremental
1. Introduction
2. Population / Sample & Sample Characteristics
3. Analytics Objective 1 — *[Member 1]*
4. Analytics Objective 2 — *[Member 2]*
5. Analytics Objective 3 — *Grace Sen* - Customer Demographics and Conversion
6. Analytics Objective 4 — *Sandy Zhu* - Customer Interaction and Purchase Behavior
7. Analytics Objective 5 — *Jungmin Woo* — Impact of Campaign Channel and Type on Customer Conversion
8. Conclusion
9. Appendix
:::

# Introduction

## Problem Definition

> TODO: State the business problem in 2–3 sentences. What is the
> marketing team struggling with (e.g., inefficient ad spend, unclear
> which channels convert, low email/on-site engagement)?

- Context: multi-channel digital marketing campaigns (Social Media, Email, PPC, Referral, SEO)
- The gap: TODO
- Who is affected / who benefits from solving this: TODO

## Research Objectives

::: incremental
- **RO1:** TODO — linked to AO1
- **RO2:** TODO — linked to AO2
- **RO3:** To examine whether customer demographic characteristics influence the likelihood of digital marketing conversion.
- **RO4:** To evaluate how customer interaction and previous purchasing behavior relate to short-term marketing response and customer conversion, and to identify the most important behavioral drivers of conversion.
- **RO5:** Impact of Campaign Channel and Type on Customer Conversion
:::

## Importance of the Research

- Business value: TODO (e.g., optimize ad spend allocation, prioritize high-conversion channels, grow on-site experiences that build loyalty)
- Academic / methodological value: TODO (e.g., comparing regression, classification, and ensemble methods on marketing data)
- Stakeholders who benefit: TODO

# Population / Sample

## Population / Sample

```{r}
#| label: setup
#| echo: true

library(tidyverse)
library(tidymodels)
library(vip)         # variable importance
library(DALEX)        # PDP / SHAP-style explanations
library(DALEXtra)
library(patchwork)

tidymodels_prefer()
theme_set(theme_minimal(base_size = 14))

raw_data <- read_csv("digital_marketing_campaign_dataset.csv", show_col_types = FALSE)

glimpse(raw_data)
```

- **Population:** Customers exposed to the company's digital marketing campaigns
- **Sample:** `r format(nrow(raw_data), big.mark = ",")` customers, `r ncol(raw_data)` variables
- **Sampling frame / period:** TODO (fill in if known — e.g., campaign dates, region)

## Data Cleaning

```{r}
#| label: cleaning

campaign_data <- raw_data |>
  # AdvertisingPlatform / AdvertisingTool are fully de-identified
  # (single constant value across all rows) -> not usable as predictors
  select(-CustomerID, -AdvertisingPlatform, -AdvertisingTool) |>
  mutate(
    Gender = factor(Gender),
    CampaignChannel = factor(CampaignChannel),
    CampaignType = factor(CampaignType),
    Conversion = factor(Conversion, levels = c(0, 1), labels = c("No", "Yes"))
  )

skimr::skim(campaign_data)
```

## Sample Characteristics

```{r}
#| label: sample-char-1
#| fig-width: 9
#| fig-height: 4.5

p1 <- ggplot(campaign_data, aes(Age)) +
  geom_histogram(bins = 30, fill = "#1f3864") +
  labs(title = "Age Distribution")

p2 <- ggplot(campaign_data, aes(Income)) +
  geom_histogram(bins = 30, fill = "#2e75b6") +
  labs(title = "Income Distribution")

p1 + p2
```

## Sample Characteristics (cont.)

```{r}
#| label: sample-char-2
#| fig-width: 9
#| fig-height: 4.5

p3 <- ggplot(campaign_data, aes(CampaignChannel, fill = Conversion)) +
  geom_bar(position = "fill") +
  labs(title = "Conversion Rate by Channel", y = "Proportion") +
  coord_flip()

p4 <- ggplot(campaign_data, aes(Gender, fill = Conversion)) +
  geom_bar(position = "fill") +
  labs(title = "Conversion Rate by Gender", y = "Proportion")

p3 + p4
```

- Overall conversion rate: `r scales::percent(mean(campaign_data$Conversion == "Yes"))` (class-imbalanced — relevant for classification AOs)
- TODO: add 2–3 bullet takeaways describing the sample (age range, income range, channel mix, etc.)

<!-- =================================================================== -->
<!-- AO1 — left blank for Member 1 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 1 — *[Member 1 Name]*

## AO1: blank

blank

## AO1: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO1: Data Wrangling & Visualization

blank

## AO1: Model Fitting

blank

## AO1: Prediction & Model Evaluation

blank

## AO1: Interpretation

blank

## AO1: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO2 — left blank for Member 2 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 2 — *[Member 2 Name]*

## AO2: blank

blank

## AO2: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO2: Data Wrangling & Visualization

blank

## AO2: Model Fitting

blank

## AO2: Prediction & Model Evaluation

blank

## AO2: Interpretation

blank

## AO2: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO3 — Customer Demographics and Conversion                            -->
<!-- =================================================================== -->

# Analytics Objective 3 — *Grace Sen*


```{r}
#| label: ao3-hidden-setup
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(tidymodels)
library(ranger)
library(scales)

tidymodels_prefer()
set.seed(6540)

cpp_green <- "#1E4D2B"
cpp_gold  <- "#FFB81C"
cpp_gray  <- "#5C6670"

theme_set(
  theme_minimal(base_size = 17) +
    theme(
      plot.title.position = "plot",
      plot.title = element_text(face = "bold", color = cpp_green),
      legend.position = "bottom",
      panel.grid.minor = element_blank()
    )
)

data_path <- "dataset/digital_marketing_campaign_dataset.csv"

marketing_raw <- read_csv(data_path, show_col_types = FALSE) |>
  rename_with(~ tolower(gsub("[^A-Za-z0-9]+", "_", .x)))

ao3 <- marketing_raw |>
  transmute(
    age = age,
    gender = factor(gender),
    income = income,
    conversion = factor(
      conversion,
      levels = c(1, 0),
      labels = c("Converted", "Not converted")
    )
  )

outcome_summary <- ao3 |>
  count(conversion) |>
  mutate(proportion = n / sum(n))

gender_rates <- ao3 |>
  group_by(gender) |>
  summarise(
    customers = n(),
    conversion_rate = mean(conversion == "Converted"),
    .groups = "drop"
  )

set.seed(6540)
ao3_split <- initial_split(ao3, prop = 0.75, strata = conversion)
ao3_train <- training(ao3_split)
ao3_test  <- testing(ao3_split)

ao3_recipe <- recipe(conversion ~ age + gender + income, data = ao3_train) |>
  step_unknown(all_nominal_predictors()) |>
  step_novel(all_nominal_predictors()) |>
  step_dummy(all_nominal_predictors(), one_hot = FALSE) |>
  step_zv(all_predictors()) |>
  step_normalize(all_numeric_predictors())

log_spec <- logistic_reg() |>
  set_engine("glm") |>
  set_mode("classification")

log_workflow <- workflow() |>
  add_recipe(ao3_recipe) |>
  add_model(log_spec)

log_fit <- fit(log_workflow, data = ao3_train)

set.seed(6540)
ao3_folds <- vfold_cv(ao3_train, v = 5, strata = conversion)

rf_spec <- rand_forest(
  trees = 500,
  mtry = tune(),
  min_n = tune()
) |>
  set_engine("ranger", probability = TRUE, importance = "permutation") |>
  set_mode("classification")

rf_workflow <- workflow() |>
  add_recipe(ao3_recipe) |>
  add_model(rf_spec)

rf_grid <- grid_regular(
  mtry(range = c(1L, 3L)),
  min_n(range = c(5L, 30L)),
  levels = c(mtry = 3, min_n = 4)
)

set.seed(6540)
rf_tuned <- tune_grid(
  rf_workflow,
  resamples = ao3_folds,
  grid = rf_grid,
  metrics = metric_set(roc_auc, pr_auc, bal_accuracy),
  control = control_grid(save_pred = TRUE)
)

best_rf <- select_best(rf_tuned, metric = "roc_auc")
final_rf_workflow <- finalize_workflow(rf_workflow, best_rf)
rf_fit <- fit(final_rf_workflow, data = ao3_train)

predict_with_probabilities <- function(fitted_workflow, new_data, model_name) {
  bind_cols(
    new_data |> select(conversion),
    predict(fitted_workflow, new_data, type = "class"),
    predict(fitted_workflow, new_data, type = "prob")
  ) |>
    mutate(model = model_name)
}

log_predictions <- predict_with_probabilities(
  log_fit, ao3_test, "Logistic regression"
)
rf_predictions <- predict_with_probabilities(
  rf_fit, ao3_test, "Random forest"
)

baseline_predictions <- ao3_test |>
  transmute(
    conversion,
    .pred_class = factor("Converted", levels = levels(conversion)),
    .pred_Converted = mean(ao3_train$conversion == "Converted"),
    .pred_Not.converted = 1 - .pred_Converted,
    model = "Majority baseline"
  )

all_predictions <- bind_rows(
  baseline_predictions,
  log_predictions,
  rf_predictions
)

classification_metrics <- metric_set(
  accuracy, bal_accuracy, sens, spec, precision, recall
)

class_results <- all_predictions |>
  group_by(model) |>
  classification_metrics(truth = conversion, estimate = .pred_class)

probability_results <- all_predictions |>
  group_by(model) |>
  metric_set(roc_auc, pr_auc)(
    truth = conversion,
    .pred_Converted,
    event_level = "first"
  )

model_metrics <- bind_rows(class_results, probability_results) |>
  select(model, .metric, .estimate) |>
  pivot_wider(names_from = .metric, values_from = .estimate)

best_model_row <- model_metrics |>
  filter(model != "Majority baseline") |>
  slice_max(roc_auc, n = 1, with_ties = FALSE)

log_odds_ratios <- extract_fit_parsnip(log_fit) |>
  tidy() |>
  filter(term != "(Intercept)") |>
  mutate(
    odds_ratio = exp(estimate),
    lower_95 = exp(estimate - 1.96 * std.error),
    upper_95 = exp(estimate + 1.96 * std.error)
  ) |>
  select(term, odds_ratio, lower_95, upper_95, p.value)

rf_engine <- extract_fit_engine(rf_fit)
rf_importance <- enframe(
  rf_engine$variable.importance,
  name = "feature",
  value = "importance"
) |>
  arrange(desc(importance))
```

## Do demographics help identify customers who convert? {background-color="#1E4D2B"}

### Analytics Objective 3

Examine whether **age, gender, and income** are associated with—and useful for predicting—customer conversion.

::: objective-line
**Predictors:** Age · Gender · Income\
**Outcome:** Conversion (binary classification)
:::

::: notes
My analytics objective asks whether customer demographics help explain and predict conversion. I use age, gender, and income as predictors and conversion as the binary outcome. The analysis compares an interpretable logistic regression with a nonlinear ensemble model.
:::

## AO3: Data Wrangling & Visualization — Sample and Outcome

:::::: columns
::: {.column width="48%"}
```{r}
#| fig-width: 7
#| fig-height: 4.4
ggplot(outcome_summary, aes(x = conversion, y = proportion, fill = conversion)) +
  geom_col(width = 0.62, show.legend = FALSE) +
  geom_text(
    aes(label = percent(proportion, accuracy = 0.1)),
    vjust = -0.35,
    size = 6
  ) +
  scale_fill_manual(values = c(cpp_green, cpp_gold)) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  labs(x = NULL, y = "Share of customers")
```
:::

:::: {.column width="48%"}
- **`r (nrow(ao3))` customers**
- **`r sum(is.na(ao3))` missing values** in AO3 variables
- Conversion rate: `r scales::percent(mean(ao3$conversion == "Converted"), accuracy = 0.1)`

::: key-message
Accuracy alone is misleading: predicting “Converted” for everyone already produces high accuracy.
:::

**Primary metrics:** ROC AUC, PR AUC, balanced accuracy, sensitivity, and specificity.
::::
::::::

::: notes
The dataset contains 8,000 customers and no missing values in the four variables used here. Conversion is highly imbalanced. Because almost nine out of ten customers converted, accuracy can look strong even when a model does not separate the two classes. I therefore emphasize discrimination and class-balanced metrics.
:::

## AO3: Data Wrangling & Visualization — Income and Gender

::::: columns
::: {.column width="50%"}
```{r}
#| fig-width: 6.8
#| fig-height: 4.7
ggplot(ao3, aes(x = conversion, y = income, fill = conversion)) +
  geom_boxplot(width = 0.62, alpha = 0.88, outlier.alpha = 0.18) +
  scale_fill_manual(values = c(cpp_green, cpp_gold), guide = "none") +
  scale_y_continuous(labels = dollar) +
  labs(title = "Income distributions overlap", x = NULL, y = "Annual income")
```
:::

::: {.column width="50%"}
```{r}
#| fig-width: 6.8
#| fig-height: 4.7
ggplot(gender_rates, aes(x = gender, y = conversion_rate, fill = gender)) +
  geom_col(width = 0.62, show.legend = FALSE) +
  geom_text(
    aes(label = percent(conversion_rate, accuracy = 0.01)),
    vjust = -0.35,
    size = 5.5
  ) +
  scale_fill_manual(values = c(cpp_green, cpp_gold)) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  labs(title = "Gender rates are nearly identical", x = NULL, y = "Conversion rate")
```
:::
:::::

::: takeaway
Neither income nor gender appears to distinguish converters from non-converters on its own.
:::

::: notes
The descriptive patterns already suggest weak demographic effects. Income medians and distributions substantially overlap across outcomes, while conversion rates are nearly equal across gender groups. These plots are descriptive, so the models next test whether the variables work better jointly.
:::

## AO3: Data Wrangling & Visualization — Age

```{r}
#| fig-width: 10.5
#| fig-height: 5.3
ggplot(ao3, aes(x = age, color = conversion)) +
  geom_density(linewidth = 1.5, adjust = 1.1) +
  scale_color_manual(values = c(cpp_green, cpp_gold)) +
  labs(x = "Age", y = "Density", color = NULL)
```

::: takeaway
Age provides little visible univariate discrimination across nearly the entire range.
:::

::: notes
The age density curves overlap across almost the full distribution. Taken together, the exploratory results provide little evidence that any single demographic variable strongly separates the outcome classes.
:::

## AO3: Machine Learning Methods & Model Fitting {.smaller}

:::::: columns
::: {.column width="46%"}
### Logistic regression

- Interpretable adjusted associations
- Standardized age and income
- Odds ratios with 95% confidence intervals

### Random forest

- Captures nonlinearities and interactions
- 500 trees
- Five-fold stratified cross-validation
- Tuned `mtry` and minimum node size
:::

:::: {.column width="50%"}
### Leakage-safe evaluation

1.  Stratified **75/25 train–test split**
2.  Training-only preprocessing recipe
3.  Dummy-code gender; normalize numeric predictors
4.  Tune the forest within training folds
5.  Evaluate once on the untouched test set

::: key-message
The majority-class prediction serves as the benchmark.
:::
::::
::::::

::: notes
Logistic regression provides interpretable adjusted effects. Random forest tests whether nonlinear patterns or interactions add predictive value. The split is stratified, all preprocessing is learned on the training data only, and the test data remains untouched until final evaluation.
:::

## AO3: Prediction & Model Evaluation

:::::: columns
::: {.column width="60%"}
```{r}
#| fig-width: 8
#| fig-height: 5
model_metrics |>
  filter(model != "Majority baseline") |>
  select(model, roc_auc, bal_accuracy) |>
  pivot_longer(-model, names_to = "metric", values_to = "score") |>
  mutate(metric = recode(
    metric,
    roc_auc = "ROC AUC",
    bal_accuracy = "Balanced accuracy"
  )) |>
  ggplot(aes(x = metric, y = score, fill = model)) +
  geom_col(position = position_dodge(width = 0.75), width = 0.64) +
  geom_hline(yintercept = 0.50, linetype = "dashed", color = cpp_gray) +
  geom_text(
    aes(label = number(score, accuracy = 0.001)),
    position = position_dodge(width = 0.75),
    vjust = -0.35,
    size = 5
  ) +
  scale_fill_manual(values = c(cpp_green, cpp_gold)) +
  scale_y_continuous(
    limits = c(0, max(0.70, max(model_metrics$roc_auc, na.rm = TRUE) + 0.08))
  ) +
  labs(x = NULL, y = "Test-set score", fill = NULL)
```
:::

:::: {.column width="36%"}
### Held-out conclusion

Better-performing model: **`r best_model_row$model`**

ROC AUC: `r scales::number(best_model_row$roc_auc, accuracy = 0.001)`

Balanced accuracy: `r scales::number(best_model_row$bal_accuracy, accuracy = 0.001)`

::: key-message
Scores near 0.50 indicate little ability to rank converters above non-converters.
:::
::::
::::::

::: notes
On the held-out test set, the best demographic model has an ROC AUC and balanced accuracy near 0.50. That is approximately chance-level performance. High raw accuracy would not change this conclusion because the converted class dominates the sample.
:::

## AO3: Interpretation — Logistic Regression

::::: columns
::: {.column width="62%"}
```{r}
#| fig-width: 8
#| fig-height: 5
ggplot(log_odds_ratios, aes(x = odds_ratio, y = reorder(term, odds_ratio))) +
  geom_vline(xintercept = 1, linetype = "dashed", color = cpp_gray) +
  geom_errorbarh(
    aes(xmin = lower_95, xmax = upper_95),
    height = 0.16,
    color = cpp_green,
    linewidth = 1
  ) +
  geom_point(size = 4, color = cpp_green) +
  labs(x = "Odds ratio with 95% CI", y = NULL)
```
:::

::: {.column width="34%"}
- Odds ratios near **1.00** indicate weak adjusted associations.
- Intervals crossing **1.00** indicate limited evidence after controlling for the other demographics.
- Association does not imply causation.
:::
:::::

::: notes
The logistic regression provides adjusted effects. Age and income are standardized, so each odds ratio represents a one-standard-deviation increase. Effects close to one, particularly with confidence intervals crossing one, support the same substantive conclusion as the held-out model evaluation.
:::

## AO3: Interpretation — Random Forest

:::::: columns
::: {.column width="62%"}
```{r}
#| fig-width: 8
#| fig-height: 5
ggplot(rf_importance, aes(x = importance, y = reorder(feature, importance))) +
  geom_col(fill = cpp_green, width = 0.64) +
  labs(x = "Permutation importance", y = NULL)
```
:::

:::: {.column width="34%"}
Permutation importance ranks predictors **within the fitted forest**.

::: key-message
A weak model can still rank weak predictors. Importance is relative and does not establish a business driver or causal effect.
:::
::::
::::::

::: notes
The random forest still produces a ranking because permutation importance is relative. We should not describe the top-ranked demographic as a strong driver when the entire model performs near chance. Variable importance also does not establish causality.
:::

## AO3: Summary Findings

::::: columns
::: {.column width="48%"}
### What AO3 found

- Demographic distributions overlap substantially.
- Both models showed weak test-set discrimination.
- Demographics alone are insufficient for targeting.
:::

::: {.column width="48%"}
### Business implication

- Prioritize behavioral and engagement signals.
- Use demographics for segmentation and fairness checks.
- Validate the final model on external data.
:::
:::::

**Takeaway:** Customer behavior is more promising than demographics for predicting conversion.

::: notes
The overall conclusion is that demographics alone do not meaningfully distinguish converters from non-converters. The business should prioritize engagement variables such as website visits, time on site, email activity, prior purchases, and campaign interactions. Demographics may remain useful for segmentation and fairness monitoring, but not as the primary targeting inputs.
:::


<!-- =================================================================== -->
<!-- AO4 — left blank for Member 4 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 4 — *[Member 4 Name]*

## AO4: blank

blank

## AO4: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO4:Customer Engagement, Purchase Behavior, and Marketing Outcomes

blank

## AO4: Model Fitting

blank

## AO4: Prediction & Model Evaluation

blank

## AO4: Interpretation

blank

## AO4: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO5 — Impact of Campaign Channel and Type on Customer Conversion    -->
<!-- =================================================================== -->


# Analytics Objective 5 — *Jungmin Woo*

## AO5: Campaign Performance {.smaller}

> RO5: Analyze the impact of marketing channels and campaign types on
> customer conversion.

- **IV (predictors):** `CampaignChannel`, `CampaignType` (both categorical)
- **DV (target):** `Conversion` (binary — Yes / No)
- **Problem type:** Classification
- Only these two categorical variables are used as predictors, so this AO
  isolates the effect of *channel* and *campaign type* on conversion,
  independent of demographic or on-site behavior variables

## AO5: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
- Not applicable (outcome is categorical)

### Classification-Focused Methods
- Logistic Regression
- Decision Tree (classification)

### Ensembles
- Random Forest (classification)

:::

## AO5: Data Wrangling & Visualization

```{r}
#| label: ao2-wrangle

# Missing-value check on the relevant columns
campaign_data |>
  select(CampaignChannel, CampaignType, Conversion) |>
  summarise(across(everything(), ~ sum(is.na(.))))

# Baseline conversion rate by Channel x Type
ao2_baseline <- campaign_data |>
  group_by(CampaignChannel, CampaignType) |>
  summarise(
    ConversionRate = mean(Conversion == "Yes"),
    N = n(),
    .groups = "drop"
  ) |>
  arrange(desc(ConversionRate))

ao2_baseline
```

```{r}
#| label: ao2-viz
#| fig-width: 9
#| fig-height: 5

ggplot(ao2_baseline, aes(x = CampaignChannel, y = ConversionRate, fill = CampaignType)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Conversion Rate by Channel, Segmented by Campaign Type",
    x = "Campaign Channel", y = "Conversion Rate", fill = "Campaign Type"
  ) +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

- No missing values in `CampaignChannel`, `CampaignType`, or `Conversion`
- The bar chart shows very little spread **across channels** within each campaign type (bars of the same color are roughly the same height), but a clear gap **across campaign types**: `CampaignType == "Conversion"` sits noticeably higher (~92–94%) than `Awareness`, `Consideration`, or `Retention` (~84–88%) in every channel
- This suggests campaign *type* may matter more than campaign *channel* for conversion — tested formally below

## AO5: Model Fitting

```{r}
#| label: ao2-fit

set.seed(2026)

ao2_data <- campaign_data |>
  select(CampaignChannel, CampaignType, Conversion)

# --- Data splitting ---
ao2_split <- initial_split(ao2_data, prop = 0.8, strata = Conversion)
ao2_train <- training(ao2_split)
ao2_test  <- testing(ao2_split)
ao2_folds <- vfold_cv(ao2_train, v = 5, strata = Conversion)

# --- Recipe ---
ao2_recipe <- recipe(Conversion ~ CampaignChannel + CampaignType, data = ao2_train) |>
  step_dummy(all_nominal_predictors()) |>
  step_zv(all_predictors())

# --- Model specifications ---
ao2_spec_glm <- logistic_reg() |>
  set_engine("glm") |>
  set_mode("classification")

ao2_spec_tree <- decision_tree(cost_complexity = tune(), tree_depth = tune()) |>
  set_engine("rpart") |>
  set_mode("classification")

ao2_spec_rf <- rand_forest(trees = 500, min_n = tune()) |>
  set_engine("ranger", importance = "permutation") |>
  set_mode("classification")

# --- Workflows ---
ao2_wf_glm  <- workflow() |> add_recipe(ao2_recipe) |> add_model(ao2_spec_glm)
ao2_wf_tree <- workflow() |> add_recipe(ao2_recipe) |> add_model(ao2_spec_tree)
ao2_wf_rf   <- workflow() |> add_recipe(ao2_recipe) |> add_model(ao2_spec_rf)

# --- Tuning ---
ao2_tree_res <- tune_grid(ao2_wf_tree, resamples = ao2_folds, grid = 5,
                           metrics = metric_set(roc_auc))
ao2_rf_res   <- tune_grid(ao2_wf_rf, resamples = ao2_folds, grid = 5,
                           metrics = metric_set(roc_auc))

# --- Finalize + fit ---
ao2_fit_glm  <- fit(ao2_wf_glm, data = ao2_train)
ao2_fit_tree <- finalize_workflow(ao2_wf_tree, select_best(ao2_tree_res, metric = "roc_auc")) |>
  fit(data = ao2_train)
ao2_fit_rf   <- finalize_workflow(ao2_wf_rf, select_best(ao2_rf_res, metric = "roc_auc")) |>
  fit(data = ao2_train)
```

## AO5: Prediction & Model Evaluation

```{r}
#| label: ao2-eval

ao2_class_metrics <- metric_set(accuracy, roc_auc, f_meas)

ao2_results <- bind_rows(
  augment(ao2_fit_glm,  new_data = ao2_test) |> mutate(model = "Logistic Regression"),
  augment(ao2_fit_tree, new_data = ao2_test) |> mutate(model = "Decision Tree"),
  augment(ao2_fit_rf,   new_data = ao2_test) |> mutate(model = "Random Forest")
)

ao2_metrics <- ao2_results |>
  group_by(model) |>
  ao2_class_metrics(truth = Conversion, estimate = .pred_class, .pred_Yes, event_level = "second")

ao2_metrics
```

- All three models land at essentially the same accuracy (~87.6%), which
  matches the overall base rate of `Conversion == "Yes"` in the data — the
  models are not beating a "always predict Yes" baseline on accuracy alone
- ROC AUC is low (~0.53–0.54, just above the 0.50 random-guess line),
  meaning `CampaignChannel` and `CampaignType` alone have only weak
  discriminative power for *individual-level* conversion, even though the
  group-level rates in the bar chart differ by type
- This is a common pattern: a variable can show a real, statistically
  significant *group-level* effect while still being a weak *individual-level*
  predictor, because most of the variation in who converts is driven by
  other factors (behavioral, demographic) not included in this AO by design

## AO5: Interpretation

```{r}
#| label: ao2-interpret
#| fig-width: 8
#| fig-height: 4.5

# Association test: does Channel matter? Does Type matter?
chisq.test(table(campaign_data$CampaignChannel, campaign_data$Conversion))
chisq.test(table(campaign_data$CampaignType, campaign_data$Conversion))

# Logistic regression coefficients (log-odds effect of each channel/type)
ao2_fit_glm |> tidy() |> arrange(p.value)

# Variable importance from Random Forest
ao2_fit_rf |> extract_fit_parsnip() |> vip(num_features = 10)
```

- The chi-square test for `CampaignChannel` is **not significant**
  (χ² ≈ 2.78, p ≈ 0.59) — channel choice alone shows no reliable
  association with conversion
- The chi-square test for `CampaignType` **is significant**
  (χ² ≈ 84.5, p < 0.001) — campaign type is meaningfully associated with
  conversion, driven mainly by the `"Conversion"` type having a
  substantially higher rate (~93%) than `Awareness`/`Consideration`/`Retention`
  (~84–88%)
- Random Forest variable importance should echo this: dummy variables for
  `CampaignType` should rank above `CampaignChannel` dummies

## AO5: Summary Findings

::: incremental
- **Campaign type** has a statistically significant relationship with
  conversion; **campaign channel** does not, at least on its own
- The higher conversion rate for `CampaignType == "Conversion"` campaigns
  is expected by design (these campaigns are explicitly built to drive
  conversion) but confirms the labeling is consistent with actual outcomes
- Despite the significant group-level association, channel + type alone
  give weak individual-level predictive power (ROC AUC ≈ 0.53) — they are
  not sufficient by themselves to identify which specific customers will
  convert
- **Business implication:** channel selection appears interchangeable for
  conversion purposes in this data, so budget allocation decisions should
  weigh cost-per-channel and other KPIs rather than assuming any one
  channel converts better; campaign *type* mix (more bottom-funnel
  "Conversion"-type campaigns) is the lever more strongly tied to
  conversion outcomes
:::


# Appendix

## Appendix

- **GitHub Repo:** [TODO — paste link]
- **Presentation Slides:** [TODO — paste Quarto Pub / GitHub Pages link]
- **Deployed Model (Shiny App / Vertiver):** [TODO — paste URL]

## Thank You / Q&A

::: {style="text-align: center; margin-top: 20%;"}
# Questions?

:::
