---
title: "Digital Marketing Campaign Analytics"
subtitle: "Group Project Final Report Presentation"
author:
  - "Member 1 Name"
  - "Member 2 Name"
  - "Member 3 Name"
  - "Member 4 Name"
  - "Member 5 Name"
date: today
format:
  revealjs:
    theme: simple
    slide-number: c/t
    footer: "Digital Marketing Campaign Analytics"
    transition: fade
    embed-resources: true
    code-fold: true
    code-tools: true
    scrollable: true
    toc: false
    chalkboard: true
execute:
  echo: true
  warning: false
  message: false
---

## Cover Slide {background-color="#1f3864"}

::: {style="text-align: center; margin-top: 15%; color: white;"}
# Digital Marketing Campaign Analytics
### Predicting Customer Conversion, Engagement, and ROI

**Team [TEAM NAME HERE]**

Member 1 · Member 2 · Member 3 · Member 4 · Member 5

`r format(Sys.Date(), "%B %d, %Y")`
:::

## Table of Contents

::: incremental
1. Introduction
2. Population / Sample & Sample Characteristics
3. Analytics Objective 1 — *[Member 1]*
4. Analytics Objective 2 — *[Member 2]*
5. Analytics Objective 3 — *[Member 3]*
6. Analytics Objective 4 — *[Member 4]*
7. Analytics Objective 5 — *[Member 5]* — On-Site Engagement & Loyalty
8. Conclusion
9. Appendix
:::

# Introduction

## Problem Definition

> TODO: State the business problem in 2–3 sentences. What is the
> marketing team struggling with (e.g., inefficient ad spend, unclear
> which channels convert, low email/on-site engagement)?

- Context: multi-channel digital marketing campaigns (Social Media, Email, PPC, Referral, SEO)
- The gap: TODO
- Who is affected / who benefits from solving this: TODO

## Research Objectives

::: incremental
- **RO1:** TODO — linked to AO1
- **RO2:** TODO — linked to AO2
- **RO3:** TODO — linked to AO3
- **RO4:** TODO — linked to AO4
- **RO5:** On-Site Engagement and Customer Loyalty Relationship — To examine how customer behavior patterns inside the website relate to their actual brand loyalty and social media advocacy. — linked to AO5
:::

## Importance of the Research

- Business value: TODO (e.g., optimize ad spend allocation, prioritize high-conversion channels, grow on-site experiences that build loyalty)
- Academic / methodological value: TODO (e.g., comparing regression, classification, and ensemble methods on marketing data)
- Stakeholders who benefit: TODO

# Population / Sample

## Population / Sample

```{r}
#| label: setup
#| echo: true

library(tidyverse)
library(tidymodels)
library(vip)         # variable importance
library(DALEX)        # PDP / SHAP-style explanations
library(DALEXtra)
library(patchwork)

tidymodels_prefer()
theme_set(theme_minimal(base_size = 14))

raw_data <- read_csv("digital_marketing_campaign_dataset.csv", show_col_types = FALSE)

glimpse(raw_data)
```

- **Population:** Customers exposed to the company's digital marketing campaigns
- **Sample:** `r format(nrow(raw_data), big.mark = ",")` customers, `r ncol(raw_data)` variables
- **Sampling frame / period:** TODO (fill in if known — e.g., campaign dates, region)

## Data Cleaning

```{r}
#| label: cleaning

campaign_data <- raw_data |>
  # AdvertisingPlatform / AdvertisingTool are fully de-identified
  # (single constant value across all rows) -> not usable as predictors
  select(-CustomerID, -AdvertisingPlatform, -AdvertisingTool) |>
  mutate(
    Gender = factor(Gender),
    CampaignChannel = factor(CampaignChannel),
    CampaignType = factor(CampaignType),
    Conversion = factor(Conversion, levels = c(0, 1), labels = c("No", "Yes"))
  )

skimr::skim(campaign_data)
```

## Sample Characteristics

```{r}
#| label: sample-char-1
#| fig-width: 9
#| fig-height: 4.5

p1 <- ggplot(campaign_data, aes(Age)) +
  geom_histogram(bins = 30, fill = "#1f3864") +
  labs(title = "Age Distribution")

p2 <- ggplot(campaign_data, aes(Income)) +
  geom_histogram(bins = 30, fill = "#2e75b6") +
  labs(title = "Income Distribution")

p1 + p2
```

## Sample Characteristics (cont.)

```{r}
#| label: sample-char-2
#| fig-width: 9
#| fig-height: 4.5

p3 <- ggplot(campaign_data, aes(CampaignChannel, fill = Conversion)) +
  geom_bar(position = "fill") +
  labs(title = "Conversion Rate by Channel", y = "Proportion") +
  coord_flip()

p4 <- ggplot(campaign_data, aes(Gender, fill = Conversion)) +
  geom_bar(position = "fill") +
  labs(title = "Conversion Rate by Gender", y = "Proportion")

p3 + p4
```

- Overall conversion rate: `r scales::percent(mean(campaign_data$Conversion == "Yes"))` (class-imbalanced — relevant for classification AOs)
- TODO: add 2–3 bullet takeaways describing the sample (age range, income range, channel mix, etc.)

<!-- =================================================================== -->
<!-- AO1 — left blank for Member 1 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 1 — *[Member 1 Name]*

## AO1: blank

blank

## AO1: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO1: Data Wrangling & Visualization

blank

## AO1: Model Fitting

blank

## AO1: Prediction & Model Evaluation

blank

## AO1: Interpretation

blank

## AO1: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO2 — left blank for Member 2 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 2 — *[Member 2 Name]*

## AO2: blank

blank

## AO2: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO2: Data Wrangling & Visualization

blank

## AO2: Model Fitting

blank

## AO2: Prediction & Model Evaluation

blank

## AO2: Interpretation

blank

## AO2: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO3 — left blank for Member 3 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 3 — *[Member 3 Name]*

## AO3: blank

blank

## AO3: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO3: Data Wrangling & Visualization

blank

## AO3: Model Fitting

blank

## AO3: Prediction & Model Evaluation

blank

## AO3: Interpretation

blank

## AO3: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO4 — left blank for Member 4 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 4 — *[Member 4 Name]*

## AO4: blank

blank

## AO4: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO4: Data Wrangling & Visualization

blank

## AO4: Model Fitting

blank

## AO4: Prediction & Model Evaluation

blank

## AO4: Interpretation

blank

## AO4: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO5 — On-Site Engagement & Customer Loyalty (Regression)            -->
<!-- RO5: To examine how customer behavior patterns inside the website   -->
<!-- relate to their actual brand loyalty and social media advocacy.    -->
<!-- =================================================================== -->

# Analytics Objective 5 — *[Member 5 Name]*

## AO5: On-Site Engagement and Customer Loyalty Relationship

> RO5: To examine how customer behavior patterns inside the website relate
> to their actual brand loyalty and social media advocacy.

- **Target variable:** `LoyaltyPoints` (continuous — used as the brand-loyalty proxy)
- **Problem type:** Regression
- **On-site engagement predictors:** `WebsiteVisits`, `PagesPerVisit`, `TimeOnSite`
- **Social advocacy predictor:** `SocialShares`
- **Controls:** `Age`, `Gender`, `Income`, `CampaignChannel`, `CampaignType`, `PreviousPurchases`, `EmailOpens`, `EmailClicks`

## AO5: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
- Multiple Linear Regression
- Elastic Net Regression

### Classification-Focused Methods
- Not applicable (outcome is continuous)

### Ensembles
- Random Forest (regression)

:::

## AO5: Data Wrangling & Visualization

```{r}
#| label: ao5-wrangle
#| fig-width: 9
#| fig-height: 4.5

ao5_data <- campaign_data |>
  select(LoyaltyPoints, WebsiteVisits, PagesPerVisit, TimeOnSite, SocialShares,
         EmailOpens, EmailClicks, PreviousPurchases,
         Age, Gender, Income, CampaignChannel, CampaignType)

ao5_p1 <- ggplot(ao5_data, aes(TimeOnSite, LoyaltyPoints)) +
  geom_point(alpha = 0.3, color = "#2e75b6") +
  geom_smooth(method = "lm", se = FALSE, color = "#1f3864") +
  labs(title = "Loyalty Points vs. Time on Site")

ao5_p2 <- ggplot(ao5_data, aes(SocialShares, LoyaltyPoints)) +
  geom_point(alpha = 0.3, color = "#2e75b6") +
  geom_smooth(method = "lm", se = FALSE, color = "#1f3864") +
  labs(title = "Loyalty Points vs. Social Shares")

ao5_p3 <- ggplot(ao5_data, aes(WebsiteVisits, LoyaltyPoints)) +
  geom_point(alpha = 0.3, color = "#2e75b6") +
  geom_smooth(method = "lm", se = FALSE, color = "#1f3864") +
  labs(title = "Loyalty Points vs. Website Visits")

ao5_p4 <- ggplot(ao5_data, aes(PagesPerVisit, LoyaltyPoints)) +
  geom_point(alpha = 0.3, color = "#2e75b6") +
  geom_smooth(method = "lm", se = FALSE, color = "#1f3864") +
  labs(title = "Loyalty Points vs. Pages per Visit")

(ao5_p1 + ao5_p2) / (ao5_p3 + ao5_p4)
```

```{r}
#| label: ao5-corr
#| fig-width: 7
#| fig-height: 6

ao5_data |>
  select(where(is.numeric)) |>
  cor() |>
  as.data.frame() |>
  rownames_to_column("var1") |>
  pivot_longer(-var1, names_to = "var2", values_to = "corr") |>
  ggplot(aes(var1, var2, fill = corr)) +
  geom_tile() +
  scale_fill_gradient2(low = "#c00000", mid = "white", high = "#1f3864", midpoint = 0) +
  labs(title = "Correlation Matrix — On-Site Behavior & Loyalty", x = NULL, y = NULL) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

- Correlations between `LoyaltyPoints` and every on-site/engagement variable are effectively zero (all |r| < 0.02: `TimeOnSite` −0.011, `PagesPerVisit` −0.013, `WebsiteVisits` 0.003, `SocialShares` −0.005)
- The scatterplots show flat clouds with no visible linear or curved trend for any predictor
- This is worth flagging early: on-site behavior and social advocacy do **not** show an obvious raw association with `LoyaltyPoints` in this sample — the model-fitting step below tests whether a combination of variables (or a non-linear model) can pick up a relationship the simple correlations miss

## AO5: Model Fitting

```{r}
#| label: ao5-fit

set.seed(2026)

# --- Data splitting ---
ao5_split <- initial_split(ao5_data, prop = 0.8)
ao5_train <- training(ao5_split)
ao5_test  <- testing(ao5_split)
ao5_folds <- vfold_cv(ao5_train, v = 5)

# --- Recipe ---
ao5_recipe <- recipe(LoyaltyPoints ~ ., data = ao5_train) |>
  step_dummy(all_nominal_predictors()) |>
  step_zv(all_predictors()) |>
  step_normalize(all_numeric_predictors())

# --- Model specifications ---
ao5_spec_lm <- linear_reg() |>
  set_engine("lm") |>
  set_mode("regression")

ao5_spec_enet <- linear_reg(penalty = tune(), mixture = tune()) |>  # elastic net
  set_engine("glmnet") |>
  set_mode("regression")

ao5_spec_rf <- rand_forest(trees = 500, mtry = tune(), min_n = tune()) |>
  set_engine("ranger", importance = "permutation") |>
  set_mode("regression")

# --- Workflows ---
ao5_wf_lm   <- workflow() |> add_recipe(ao5_recipe) |> add_model(ao5_spec_lm)
ao5_wf_enet <- workflow() |> add_recipe(ao5_recipe) |> add_model(ao5_spec_enet)
ao5_wf_rf   <- workflow() |> add_recipe(ao5_recipe) |> add_model(ao5_spec_rf)

# --- Tuning ---
ao5_enet_res <- tune_grid(ao5_wf_enet, resamples = ao5_folds, grid = 10,
                           metrics = metric_set(rmse))
ao5_rf_res   <- tune_grid(ao5_wf_rf, resamples = ao5_folds, grid = 5,
                           metrics = metric_set(rmse))

# --- Finalize + fit ---
ao5_fit_lm   <- fit(ao5_wf_lm, data = ao5_train)
ao5_fit_enet <- finalize_workflow(ao5_wf_enet, select_best(ao5_enet_res, metric = "rmse")) |>
  fit(data = ao5_train)
ao5_fit_rf   <- finalize_workflow(ao5_wf_rf, select_best(ao5_rf_res, metric = "rmse")) |>
  fit(data = ao5_train)
```

## AO5: Prediction & Model Evaluation

```{r}
#| label: ao5-eval

ao5_reg_metrics <- metric_set(rmse, rsq, mae)

ao5_results <- bind_rows(
  augment(ao5_fit_lm,   new_data = ao5_test) |> mutate(model = "Linear Regression"),
  augment(ao5_fit_enet, new_data = ao5_test) |> mutate(model = "Elastic Net"),
  augment(ao5_fit_rf,   new_data = ao5_test) |> mutate(model = "Random Forest")
)

ao5_metrics <- ao5_results |>
  group_by(model) |>
  ao5_reg_metrics(truth = LoyaltyPoints, estimate = .pred)

ao5_metrics

ggplot(ao5_results, aes(.pred, LoyaltyPoints)) +
  geom_point(alpha = 0.3) +
  geom_abline(linetype = "dashed", color = "red") +
  facet_wrap(~model) +
  labs(title = "Predicted vs. Actual Loyalty Points")
```

- All three models perform essentially the same as guessing the mean of `LoyaltyPoints` for every customer: RMSE ≈ 1,440 points, MAE ≈ 1,245 points, and **R² is at or below zero** (Linear Regression R² ≈ −0.005, Elastic Net R² ≈ 0.000, Random Forest R² ≈ −0.02)
- An R² at/below zero means the models explain none of the variance in `LoyaltyPoints` — they do no better (Random Forest slightly worse, due to overfitting noise) than a naive baseline
- The predicted-vs-actual plot should show a flat horizontal band of predictions around the mean, with no diagonal alignment to the actual values
- **Takeaway for RO5:** in this sample, on-site engagement behavior and social advocacy do not measurably predict `LoyaltyPoints`

## AO5: Interpretation

```{r}
#| label: ao5-interpret
#| fig-width: 8
#| fig-height: 4.5

# Variable importance — which on-site/advocacy behaviors matter most
ao5_fit_rf |> extract_fit_parsnip() |> vip(num_features = 10)

# Coefficients from the linear model (direction & magnitude of relationships)
ao5_fit_lm |> tidy() |> arrange(desc(abs(estimate)))
```

```{r}
#| label: ao5-pdp
#| fig-width: 9
#| fig-height: 4.5

ao5_explainer <- explain_tidymodels(
  ao5_fit_rf,
  data = ao5_train |> select(-LoyaltyPoints),
  y = ao5_train$LoyaltyPoints,
  verbose = FALSE
)

pdp_time    <- model_profile(ao5_explainer, variables = "TimeOnSite")
pdp_shares  <- model_profile(ao5_explainer, variables = "SocialShares")

(plot(pdp_time) + labs(title = "PDP: Time on Site")) +
  (plot(pdp_shares) + labs(title = "PDP: Social Shares"))
```

- Random Forest variable importance ranks `PagesPerVisit`, `TimeOnSite`, `Income`, and `SocialShares` highest, but this reflects relative importance *within a model that has no real predictive power* (R² ≈ −0.02) — it should not be read as evidence these variables actually drive loyalty
- The linear model's largest coefficients belong to `CampaignChannel` and `Gender`, not the on-site/advocacy variables central to RO5, and none of the on-site coefficients are large relative to their scale
- The PDP lines for `TimeOnSite` and `SocialShares` should come out nearly flat, consistent with the near-zero correlations and R² found above — there is no meaningful non-linear relationship either

## AO5: Summary Findings

::: incremental
- On-site engagement (`TimeOnSite`, `PagesPerVisit`, `WebsiteVisits`) shows **no meaningful relationship** with `LoyaltyPoints` in this dataset — correlations are all under 0.02 in magnitude
- Social media advocacy (`SocialShares`) similarly shows **no independent relationship** with loyalty, before or after controlling for on-site behavior and demographics
- All three models (Linear Regression, Elastic Net, Random Forest) perform at or worse than a naive mean-prediction baseline (R² ≤ 0), so none is meaningfully "best" — this is a **null result**, not a modeling failure to fix
- **Business implication:** `LoyaltyPoints`, as recorded in this dataset, does not appear to be driven by on-site behavior or social advocacy — before investing in on-site experience changes to grow loyalty, the business should verify how `LoyaltyPoints` is actually assigned (e.g., a points-per-purchase program) and consider testing a more direct loyalty measure (repeat purchase rate, NPS, tenure) against engagement behavior
:::

<!-- =================================================================== -->

# Conclusion

## Key Findings

::: incremental
- TODO: synthesize the single most important finding from each AO (5 bullets)
:::

## Recommendations for Businesses

::: incremental
- TODO: 3–5 concrete, actionable recommendations tied back to the AOs
:::

## Limitations and Directions for Future Research

::: {.columns}
::: {.column width="50%"}
**Limitations**

- TODO (e.g., single snapshot in time, de-identified platform/tool fields, class imbalance, LoyaltyPoints as an imperfect loyalty proxy)
:::
::: {.column width="50%"}
**Future Research**

- TODO (e.g., time-series campaign data, causal experiments / A-B tests, direct loyalty survey measures)
:::
:::

# Appendix

## Appendix

- **GitHub Repo:** [TODO — paste link]
- **Presentation Slides:** [TODO — paste Quarto Pub / GitHub Pages link]
- **Deployed Model (Shiny App / Vertiver):** [TODO — paste URL]

## Thank You / Q&A

::: {style="text-align: center; margin-top: 20%;"}
# Questions?

Team [TEAM NAME] — Digital Marketing Campaign Analytics
:::
