---
title: "Digital Marketing Campaign Analytics"
subtitle: "Group Project Final Report Presentation"
author:
  - "Member 1 Name"
  - "Member 2 Name"
  - "Member 3 Name"
  - "Sandy Zhu"
  - "Jungmin Woo"
date: today
format:
  revealjs:
    theme: simple
    slide-number: c/t
    footer: "Digital Marketing Campaign Analytics"
    transition: fade
    embed-resources: false
    code-fold: true
    code-tools: true
    scrollable: true
    toc: false
    chalkboard: true
execute:
  echo: true
  warning: false
  message: false
---

## Cover Slide {background-color="#1f3864"}

::: {style="text-align: center; margin-top: 15%; color: white;"}
# Digital Marketing Campaign Analytics
### Predicting Customer Conversion, Engagement, and ROI


`r format(Sys.Date(), "%B %d, %Y")`
:::

## Table of Contents

::: incremental
1. Introduction
2. Population / Sample & Sample Characteristics
3. Analytics Objective 1 — *[Member 1]*
4. Analytics Objective 2 — *[Member 2]*
5. Analytics Objective 3 — *[Member 3]*
6. Analytics Objective 4 — *Sandy Zhu* - Customer Interaction and Purchase Behavior
7. Analytics Objective 5 — *Jungmin Woo* — 
8. Conclusion
9. Appendix
:::

# Introduction

## Problem Definition

> TODO: State the business problem in 2–3 sentences. What is the
> marketing team struggling with (e.g., inefficient ad spend, unclear
> which channels convert, low email/on-site engagement)?

- Context: multi-channel digital marketing campaigns (Social Media, Email, PPC, Referral, SEO)
- The gap: TODO
- Who is affected / who benefits from solving this: TODO

## Research Objectives

::: incremental
- **RO1:** TODO — linked to AO1
- **RO2:** TODO — linked to AO2
- **RO3:** TODO — linked to AO3
- **RO4:** To evaluate how customer interaction and previous purchasing behavior relate to short-term marketing response and customer conversion, and to identify the most important behavioral drivers of conversion.
- **RO5:** On-Site Engagement and Customer Loyalty Relationship — To examine how customer behavior patterns inside the website relate to their actual brand loyalty and social media advocacy. — linked to AO5
:::

## Importance of the Research

- Business value: TODO (e.g., optimize ad spend allocation, prioritize high-conversion channels, grow on-site experiences that build loyalty)
- Academic / methodological value: TODO (e.g., comparing regression, classification, and ensemble methods on marketing data)
- Stakeholders who benefit: TODO

# Population / Sample

## Population / Sample

```{r}
#| label: setup
#| echo: true

library(tidyverse)
library(tidymodels)
library(vip)         # variable importance
library(DALEX)        # PDP / SHAP-style explanations
library(DALEXtra)
library(patchwork)

tidymodels_prefer()
theme_set(theme_minimal(base_size = 14))

raw_data <- read_csv("digital_marketing_campaign_dataset.csv", show_col_types = FALSE)

glimpse(raw_data)
```

- **Population:** Customers exposed to the company's digital marketing campaigns
- **Sample:** `r format(nrow(raw_data), big.mark = ",")` customers, `r ncol(raw_data)` variables
- **Sampling frame / period:** TODO (fill in if known — e.g., campaign dates, region)

## Data Cleaning

```{r}
#| label: cleaning

campaign_data <- raw_data |>
  # AdvertisingPlatform / AdvertisingTool are fully de-identified
  # (single constant value across all rows) -> not usable as predictors
  select(-CustomerID, -AdvertisingPlatform, -AdvertisingTool) |>
  mutate(
    Gender = factor(Gender),
    CampaignChannel = factor(CampaignChannel),
    CampaignType = factor(CampaignType),
    Conversion = factor(Conversion, levels = c(0, 1), labels = c("No", "Yes"))
  )

skimr::skim(campaign_data)
```

## Sample Characteristics

```{r}
#| label: sample-char-1
#| fig-width: 9
#| fig-height: 4.5

p1 <- ggplot(campaign_data, aes(Age)) +
  geom_histogram(bins = 30, fill = "#1f3864") +
  labs(title = "Age Distribution")

p2 <- ggplot(campaign_data, aes(Income)) +
  geom_histogram(bins = 30, fill = "#2e75b6") +
  labs(title = "Income Distribution")

p1 + p2
```

## Sample Characteristics (cont.)

```{r}
#| label: sample-char-2
#| fig-width: 9
#| fig-height: 4.5

p3 <- ggplot(campaign_data, aes(CampaignChannel, fill = Conversion)) +
  geom_bar(position = "fill") +
  labs(title = "Conversion Rate by Channel", y = "Proportion") +
  coord_flip()

p4 <- ggplot(campaign_data, aes(Gender, fill = Conversion)) +
  geom_bar(position = "fill") +
  labs(title = "Conversion Rate by Gender", y = "Proportion")

p3 + p4
```

- Overall conversion rate: `r scales::percent(mean(campaign_data$Conversion == "Yes"))` (class-imbalanced — relevant for classification AOs)
- TODO: add 2–3 bullet takeaways describing the sample (age range, income range, channel mix, etc.)

<!-- =================================================================== -->
<!-- AO1 — left blank for Member 1 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 1 — *[Member 1 Name]*

## AO1: blank

blank

## AO1: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO1: Data Wrangling & Visualization

blank

## AO1: Model Fitting

blank

## AO1: Prediction & Model Evaluation

blank

## AO1: Interpretation

blank

## AO1: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO2 — left blank for Member 2 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 2 — *[Member 2 Name]*

## AO2: blank

blank

## AO2: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO2: Data Wrangling & Visualization

blank

## AO2: Model Fitting

blank

## AO2: Prediction & Model Evaluation

blank

## AO2: Interpretation

blank

## AO2: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO3 — left blank for Member 3 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 3 — *[Member 3 Name]*

## AO3: blank

blank

## AO3: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO3: Data Wrangling & Visualization

blank

## AO3: Model Fitting

blank

## AO3: Prediction & Model Evaluation

blank

## AO3: Interpretation

blank

## AO3: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO4 — left blank for Member 4 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 4 — *[Member 4 Name]*

## AO4: blank

blank

## AO4: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO4:Customer Engagement, Purchase Behavior, and Marketing Outcomes

blank

## AO4: Model Fitting

blank

## AO4: Prediction & Model Evaluation

blank

## AO4: Interpretation

blank

## AO4: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO5 — On-Site Engagement & Customer Loyalty (Regression)            -->
<!-- RO5: To examine how customer behavior patterns inside the website   -->
<!-- relate to their actual brand loyalty and social media advocacy.    -->
<!-- =================================================================== -->

# Analytics Objective 5 — **



# Appendix

## Appendix

- **GitHub Repo:** [TODO — paste link]
- **Presentation Slides:** [TODO — paste Quarto Pub / GitHub Pages link]
- **Deployed Model (Shiny App / Vertiver):** [TODO — paste URL]

## Thank You / Q&A

::: {style="text-align: center; margin-top: 20%;"}
# Questions?

:::
