---
title: "Digital Marketing Campaign Analytics"
subtitle: "Group Project Final Report Presentation"
author:
  - "Member 1 Name"
  - "Member 2 Name"
  - "Member 3 Name"
  - "Sandy Zhu"
  - "Jungmin Woo"
date: today
format:
  revealjs:
    theme: simple
    slide-number: c/t
    footer: "Digital Marketing Campaign Analytics"
    transition: fade
    embed-resources: false
    code-fold: true
    code-tools: true
    scrollable: true
    toc: false
    chalkboard: true
execute:
  echo: true
  warning: false
  message: false
---

## Cover Slide {background-color="#1f3864"}

::: {style="text-align: center; margin-top: 15%; color: white;"}
# Digital Marketing Campaign Analytics
### Predicting Customer Conversion, Engagement, and ROI


`r format(Sys.Date(), "%B %d, %Y")`
:::

## Table of Contents

::: incremental
1. Introduction
2. Population / Sample & Sample Characteristics
3. Analytics Objective 1 — *[Member 1]*
4. Analytics Objective 2 — *[Member 2]*
5. Analytics Objective 3 — *[Member 3]*
6. Analytics Objective 4 — *Sandy Zhu* - Customer Interaction and Purchase Behavior
7. Analytics Objective 5 — *Jungmin Woo* — 
8. Conclusion
9. Appendix
:::

# Introduction

## Problem Definition

> TODO: State the business problem in 2–3 sentences. What is the
> marketing team struggling with (e.g., inefficient ad spend, unclear
> which channels convert, low email/on-site engagement)?

- Context: multi-channel digital marketing campaigns (Social Media, Email, PPC, Referral, SEO)
- The gap: TODO
- Who is affected / who benefits from solving this: TODO

## Research Objectives

::: incremental
- **RO1:** TODO — linked to AO1
- **RO2:** TODO — linked to AO2
- **RO3:** TODO — linked to AO3
- **RO4:** To evaluate how customer interaction and previous purchasing behavior relate to short-term marketing response and customer conversion, and to identify the most important behavioral drivers of conversion.
- **RO5:** Impact of Campaign Channel and Type on Customer Conversion
:::

## Importance of the Research

- Business value: TODO (e.g., optimize ad spend allocation, prioritize high-conversion channels, grow on-site experiences that build loyalty)
- Academic / methodological value: TODO (e.g., comparing regression, classification, and ensemble methods on marketing data)
- Stakeholders who benefit: TODO

# Population / Sample

## Population / Sample

```{r}
#| label: setup
#| echo: true

library(tidyverse)
library(tidymodels)
library(vip)         # variable importance
library(DALEX)        # PDP / SHAP-style explanations
library(DALEXtra)
library(patchwork)

tidymodels_prefer()
theme_set(theme_minimal(base_size = 14))

raw_data <- read_csv("digital_marketing_campaign_dataset.csv", show_col_types = FALSE)

glimpse(raw_data)
```

- **Population:** Customers exposed to the company's digital marketing campaigns
- **Sample:** `r format(nrow(raw_data), big.mark = ",")` customers, `r ncol(raw_data)` variables
- **Sampling frame / period:** TODO (fill in if known — e.g., campaign dates, region)

## Data Cleaning

```{r}
#| label: cleaning

campaign_data <- raw_data |>
  # AdvertisingPlatform / AdvertisingTool are fully de-identified
  # (single constant value across all rows) -> not usable as predictors
  select(-CustomerID, -AdvertisingPlatform, -AdvertisingTool) |>
  mutate(
    Gender = factor(Gender),
    CampaignChannel = factor(CampaignChannel),
    CampaignType = factor(CampaignType),
    Conversion = factor(Conversion, levels = c(0, 1), labels = c("No", "Yes"))
  )

skimr::skim(campaign_data)
```

## Sample Characteristics

```{r}
#| label: sample-char-1
#| fig-width: 9
#| fig-height: 4.5

p1 <- ggplot(campaign_data, aes(Age)) +
  geom_histogram(bins = 30, fill = "#1f3864") +
  labs(title = "Age Distribution")

p2 <- ggplot(campaign_data, aes(Income)) +
  geom_histogram(bins = 30, fill = "#2e75b6") +
  labs(title = "Income Distribution")

p1 + p2
```

## Sample Characteristics (cont.)

```{r}
#| label: sample-char-2
#| fig-width: 9
#| fig-height: 4.5

p3 <- ggplot(campaign_data, aes(CampaignChannel, fill = Conversion)) +
  geom_bar(position = "fill") +
  labs(title = "Conversion Rate by Channel", y = "Proportion") +
  coord_flip()

p4 <- ggplot(campaign_data, aes(Gender, fill = Conversion)) +
  geom_bar(position = "fill") +
  labs(title = "Conversion Rate by Gender", y = "Proportion")

p3 + p4
```

- Overall conversion rate: `r scales::percent(mean(campaign_data$Conversion == "Yes"))` (class-imbalanced — relevant for classification AOs)
- TODO: add 2–3 bullet takeaways describing the sample (age range, income range, channel mix, etc.)

<!-- =================================================================== -->
<!-- AO1 — left blank for Member 1 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 1 — *[Member 1 Name]*

## AO1: blank

blank

## AO1: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO1: Data Wrangling & Visualization

blank

## AO1: Model Fitting

blank

## AO1: Prediction & Model Evaluation

blank

## AO1: Interpretation

blank

## AO1: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO2 — left blank for Member 2 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 2 — *[Member 2 Name]*

## AO2: blank

blank

## AO2: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO2: Data Wrangling & Visualization

blank

## AO2: Model Fitting

blank

## AO2: Prediction & Model Evaluation

blank

## AO2: Interpretation

blank

## AO2: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO3 — left blank for Member 3 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 3 — *[Member 3 Name]*

## AO3: blank

blank

## AO3: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO3: Data Wrangling & Visualization

blank

## AO3: Model Fitting

blank

## AO3: Prediction & Model Evaluation

blank

## AO3: Interpretation

blank

## AO3: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO4 — left blank for Member 4 to fill in                            -->
<!-- =================================================================== -->

# Analytics Objective 4 — *[Member 4 Name]*

## AO4: blank

blank

## AO4: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
blank

### Classification-Focused Methods
blank

### Ensembles
blank

:::

## AO4:Customer Engagement, Purchase Behavior, and Marketing Outcomes

blank

## AO4: Model Fitting

blank

## AO4: Prediction & Model Evaluation

blank

## AO4: Interpretation

blank

## AO4: Summary Findings

blank

<!-- =================================================================== -->
<!-- AO5 — Impact of Campaign Channel and Type on Customer Conversion    -->
<!-- =================================================================== -->


# Analytics Objective 5 — *Jungmin Woo*

## AO5: Campaign Performance {.smaller}

> RO5: Analyze the impact of marketing channels and campaign types on
> customer conversion.

- **IV (predictors):** `CampaignChannel`, `CampaignType` (both categorical)
- **DV (target):** `Conversion` (binary — Yes / No)
- **Problem type:** Classification
- Only these two categorical variables are used as predictors, so this AO
  isolates the effect of *channel* and *campaign type* on conversion,
  independent of demographic or on-site behavior variables

## AO5: Machine Learning Methods to be Used

::: {.panel-tabset}

### Regression-Focused Methods
- Not applicable (outcome is categorical)

### Classification-Focused Methods
- Logistic Regression
- Decision Tree (classification)

### Ensembles
- Random Forest (classification)

:::

## AO5: Data Wrangling & Visualization

```{r}
#| label: ao2-wrangle

# Missing-value check on the relevant columns
campaign_data |>
  select(CampaignChannel, CampaignType, Conversion) |>
  summarise(across(everything(), ~ sum(is.na(.))))

# Baseline conversion rate by Channel x Type
ao2_baseline <- campaign_data |>
  group_by(CampaignChannel, CampaignType) |>
  summarise(
    ConversionRate = mean(Conversion == "Yes"),
    N = n(),
    .groups = "drop"
  ) |>
  arrange(desc(ConversionRate))

ao2_baseline
```

```{r}
#| label: ao2-viz
#| fig-width: 9
#| fig-height: 5

ggplot(ao2_baseline, aes(x = CampaignChannel, y = ConversionRate, fill = CampaignType)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Conversion Rate by Channel, Segmented by Campaign Type",
    x = "Campaign Channel", y = "Conversion Rate", fill = "Campaign Type"
  ) +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

- No missing values in `CampaignChannel`, `CampaignType`, or `Conversion`
- The bar chart shows very little spread **across channels** within each campaign type (bars of the same color are roughly the same height), but a clear gap **across campaign types**: `CampaignType == "Conversion"` sits noticeably higher (~92–94%) than `Awareness`, `Consideration`, or `Retention` (~84–88%) in every channel
- This suggests campaign *type* may matter more than campaign *channel* for conversion — tested formally below

## AO5: Model Fitting

```{r}
#| label: ao2-fit

set.seed(2026)

ao2_data <- campaign_data |>
  select(CampaignChannel, CampaignType, Conversion)

# --- Data splitting ---
ao2_split <- initial_split(ao2_data, prop = 0.8, strata = Conversion)
ao2_train <- training(ao2_split)
ao2_test  <- testing(ao2_split)
ao2_folds <- vfold_cv(ao2_train, v = 5, strata = Conversion)

# --- Recipe ---
ao2_recipe <- recipe(Conversion ~ CampaignChannel + CampaignType, data = ao2_train) |>
  step_dummy(all_nominal_predictors()) |>
  step_zv(all_predictors())

# --- Model specifications ---
ao2_spec_glm <- logistic_reg() |>
  set_engine("glm") |>
  set_mode("classification")

ao2_spec_tree <- decision_tree(cost_complexity = tune(), tree_depth = tune()) |>
  set_engine("rpart") |>
  set_mode("classification")

ao2_spec_rf <- rand_forest(trees = 500, min_n = tune()) |>
  set_engine("ranger", importance = "permutation") |>
  set_mode("classification")

# --- Workflows ---
ao2_wf_glm  <- workflow() |> add_recipe(ao2_recipe) |> add_model(ao2_spec_glm)
ao2_wf_tree <- workflow() |> add_recipe(ao2_recipe) |> add_model(ao2_spec_tree)
ao2_wf_rf   <- workflow() |> add_recipe(ao2_recipe) |> add_model(ao2_spec_rf)

# --- Tuning ---
ao2_tree_res <- tune_grid(ao2_wf_tree, resamples = ao2_folds, grid = 5,
                           metrics = metric_set(roc_auc))
ao2_rf_res   <- tune_grid(ao2_wf_rf, resamples = ao2_folds, grid = 5,
                           metrics = metric_set(roc_auc))

# --- Finalize + fit ---
ao2_fit_glm  <- fit(ao2_wf_glm, data = ao2_train)
ao2_fit_tree <- finalize_workflow(ao2_wf_tree, select_best(ao2_tree_res, metric = "roc_auc")) |>
  fit(data = ao2_train)
ao2_fit_rf   <- finalize_workflow(ao2_wf_rf, select_best(ao2_rf_res, metric = "roc_auc")) |>
  fit(data = ao2_train)
```

## AO5: Prediction & Model Evaluation

```{r}
#| label: ao2-eval

ao2_class_metrics <- metric_set(accuracy, roc_auc, f_meas)

ao2_results <- bind_rows(
  augment(ao2_fit_glm,  new_data = ao2_test) |> mutate(model = "Logistic Regression"),
  augment(ao2_fit_tree, new_data = ao2_test) |> mutate(model = "Decision Tree"),
  augment(ao2_fit_rf,   new_data = ao2_test) |> mutate(model = "Random Forest")
)

ao2_metrics <- ao2_results |>
  group_by(model) |>
  ao2_class_metrics(truth = Conversion, estimate = .pred_class, .pred_Yes, event_level = "second")

ao2_metrics
```

- All three models land at essentially the same accuracy (~87.6%), which
  matches the overall base rate of `Conversion == "Yes"` in the data — the
  models are not beating a "always predict Yes" baseline on accuracy alone
- ROC AUC is low (~0.53–0.54, just above the 0.50 random-guess line),
  meaning `CampaignChannel` and `CampaignType` alone have only weak
  discriminative power for *individual-level* conversion, even though the
  group-level rates in the bar chart differ by type
- This is a common pattern: a variable can show a real, statistically
  significant *group-level* effect while still being a weak *individual-level*
  predictor, because most of the variation in who converts is driven by
  other factors (behavioral, demographic) not included in this AO by design

## AO5: Interpretation

```{r}
#| label: ao2-interpret
#| fig-width: 8
#| fig-height: 4.5

# Association test: does Channel matter? Does Type matter?
chisq.test(table(campaign_data$CampaignChannel, campaign_data$Conversion))
chisq.test(table(campaign_data$CampaignType, campaign_data$Conversion))

# Logistic regression coefficients (log-odds effect of each channel/type)
ao2_fit_glm |> tidy() |> arrange(p.value)

# Variable importance from Random Forest
ao2_fit_rf |> extract_fit_parsnip() |> vip(num_features = 10)
```

- The chi-square test for `CampaignChannel` is **not significant**
  (χ² ≈ 2.78, p ≈ 0.59) — channel choice alone shows no reliable
  association with conversion
- The chi-square test for `CampaignType` **is significant**
  (χ² ≈ 84.5, p < 0.001) — campaign type is meaningfully associated with
  conversion, driven mainly by the `"Conversion"` type having a
  substantially higher rate (~93%) than `Awareness`/`Consideration`/`Retention`
  (~84–88%)
- Random Forest variable importance should echo this: dummy variables for
  `CampaignType` should rank above `CampaignChannel` dummies

## AO5: Summary Findings

::: incremental
- **Campaign type** has a statistically significant relationship with
  conversion; **campaign channel** does not, at least on its own
- The higher conversion rate for `CampaignType == "Conversion"` campaigns
  is expected by design (these campaigns are explicitly built to drive
  conversion) but confirms the labeling is consistent with actual outcomes
- Despite the significant group-level association, channel + type alone
  give weak individual-level predictive power (ROC AUC ≈ 0.53) — they are
  not sufficient by themselves to identify which specific customers will
  convert
- **Business implication:** channel selection appears interchangeable for
  conversion purposes in this data, so budget allocation decisions should
  weigh cost-per-channel and other KPIs rather than assuming any one
  channel converts better; campaign *type* mix (more bottom-funnel
  "Conversion"-type campaigns) is the lever more strongly tied to
  conversion outcomes
:::


# Appendix

## Appendix

- **GitHub Repo:** [TODO — paste link]
- **Presentation Slides:** [TODO — paste Quarto Pub / GitHub Pages link]
- **Deployed Model (Shiny App / Vertiver):** [TODO — paste URL]

## Thank You / Q&A

::: {style="text-align: center; margin-top: 20%;"}
# Questions?

:::
