---
title: "Digital Marketing Campaign Analytics"
subtitle: "Group Project Final Report Presentation"

author:
  - "Yushan Huang"
  - "Sora Hosoda"
  - "Grace Sen"
  - "Sandy Zhu"
  - "Jungmin Woo"

date: today

format:
  revealjs:
    theme: simple
    slide-number: c/t
    transition: fade
    embed-resources: false
    code-fold: true
    code-tools: true
    scrollable: true
    toc: false
    chalkboard: true
    width: 1600
    height: 900
    margin: 0.06
editor: 
  markdown: 
    wrap: 72
---

## Table of Contents

::: incremental
1.  Introduction
2.  Population / Sample & Sample Characteristics
3.  Analytics Objective 1 — *Yushan Huang* - Marketing Investment &
    On-Site Engagement
4.  Analytics Objective 2 — *Jungmin Woo* - To analyze the impact of
    marketing channels and campaign types on customer conversion
5.  Analytics Objective 3 — *Grace Sen* - Customer Demographics and
    Conversion
6.  Analytics Objective 4 — *Sandy Zhu* - Customer Interaction and
    Purchase Behavior
7.  Analytics Objective 5 — *Sora Hosoda* - Predictive Analytics
8.  Conclusion
9.  Appendix
:::

# Introduction

## Problem Definition

Digital marketing teams use multiple campaign channels and campaign
strategies to reach customers, but it is not always clear which
approaches are most strongly associated with customer conversion.
Without data-driven evidence, marketing resources may be allocated to
channels or campaign types that do not meaningfully improve conversion
outcomes.

- **Context:** The dataset represents multi-channel digital marketing
  campaigns, including Social Media, Email, PPC, Referral, and SEO.
- **Business gap:** Marketers need clearer evidence about which campaign
  characteristics and customer behaviors are associated with successful
  conversion.
- **Decision need:** Identify actionable patterns that can support
  better campaign design, targeting, engagement, and resource
  allocation.

## Research Objectives

::: incremental
- **RO1:** To evaluate whether advertising spend and on-site engagement
  signals can identify customers who are more likely to convert.
- **RO2:** Impact of Campaign Channel and Type on Customer Conversion
- **RO3:** To examine whether customer demographic characteristics
  influence the likelihood of digital marketing conversion.
- **RO4:** To evaluate how customer interaction and previous purchasing
  behavior relate to short-term marketing response and customer
  conversion, and to identify the most important behavioral drivers of
  conversion.
- **RO5:** To develop a predictive model that identifies the most useful
  factors for predicting customer conversion using customer
  demographics, campaign information, engagement variables, and purchase
  history.
:::

## Importance of the Research

- **Improve marketing effectiveness:** Understanding the factors
  associated with conversion can help marketers make more informed
  decisions about campaign strategy and customer targeting.
- **Support resource allocation:** Comparing marketing channels and
  campaign types can reveal whether conversion outcomes differ
  meaningfully across marketing approaches.
- **Generate customer insights:** Examining engagement, purchasing
  behavior, and loyalty-related measures can help explain how customers
  respond throughout the digital marketing journey.
- **Apply predictive analytics:** Classification and ensemble methods
  provide a systematic way to evaluate conversion patterns and assess
  how useful marketing and behavioral variables are for prediction.
- **Business stakeholders:** The findings can support marketing
  managers, campaign planners, and customer analytics teams when
  designing and evaluating future campaigns.

# Population / Sample

## Population / Sample

```{r}
#| label: setup
#| echo: true

library(tidyverse)
library(tidymodels)
library(vip)         # variable importance
library(DALEX)        # PDP / SHAP-style explanations
library(DALEXtra)
library(patchwork)

tidymodels_prefer()
theme_set(theme_minimal(base_size = 14))

raw_data <- read_csv("digital_marketing_campaign_dataset.csv", show_col_types = FALSE)

glimpse(raw_data)
```

- **Population:** Customers exposed to the company's digital marketing
  campaigns
- **Sample:** `r format(nrow(raw_data), big.mark = ",")` customers,
  `r ncol(raw_data)` variables
- **Sampling frame / period:** The dataset does not provide a specific
  campaign period or geographic region.

## Data Cleaning

```{r}
#| label: cleaning

campaign_data <- raw_data |>
  # AdvertisingPlatform / AdvertisingTool are fully de-identified
  # (single constant value across all rows) -> not usable as predictors
  select(-CustomerID, -AdvertisingPlatform, -AdvertisingTool) |>
  mutate(
    Gender = factor(Gender),
    CampaignChannel = factor(CampaignChannel),
    CampaignType = factor(CampaignType),
    Conversion = factor(Conversion, levels = c(0, 1), labels = c("No", "Yes"))
  )

skimr::skim(campaign_data)
```

## Sample Characteristics

```{r}
#| label: sample-char-1
#| fig-width: 9
#| fig-height: 4.5

p1 <- ggplot(campaign_data, aes(Age)) +
  geom_histogram(bins = 30, fill = "#1f3864") +
  labs(title = "Age Distribution")

p2 <- ggplot(campaign_data, aes(Income)) +
  geom_histogram(bins = 30, fill = "#2e75b6") +
  labs(title = "Income Distribution")

p1 + p2
```

## Sample Characteristics (cont.)

```{r}
#| label: sample-char-2
#| fig-width: 9
#| fig-height: 4.5

p3 <- ggplot(campaign_data, aes(CampaignChannel, fill = Conversion)) +
  geom_bar(position = "fill") +
  labs(title = "Conversion Rate by Channel", y = "Proportion") +
  coord_flip()

p4 <- ggplot(campaign_data, aes(Gender, fill = Conversion)) +
  geom_bar(position = "fill") +
  labs(title = "Conversion Rate by Gender", y = "Proportion")

p3 + p4
```

- Overall conversion rate:
  `r scales::percent(mean(campaign_data$Conversion == "Yes"))`
  (class-imbalanced — relevant for classification AOs)
- The sample includes customers across a wide range of ages and income
  levels.
- Customers were exposed to five digital marketing channels: Social
  Media, Email, PPC, Referral, and SEO.
- The overall conversion rate is approximately **87.7%**, indicating a
  strong class imbalance that should be considered when evaluating
  classification models.

<!-- =================================================================== -->

<!-- AO1 — Marketing Investment & On-Site Engagement                         -->

<!-- =================================================================== -->

# Analytics Objective 1 — *Yushan Huang*

## AO1: Marketing Investment & On-Site Engagement

> **RO1:** To evaluate whether advertising spend and on-site engagement
> signals can identify customers who are more likely to convert.

- **Target variable:** `Conversion` (No / Yes)
- **Predictors:** `AdSpend`, `ClickThroughRate`, `WebsiteVisits`,
  `PagesPerVisit`, `TimeOnSite`
- **Problem type:** Binary classification
- **Business question:** Can marketing investment and website engagement
  help identify higher-conversion customers?
- **Why this AO is distinct:** It focuses on **paid investment + on-site
  engagement**, rather than campaign type/channel (AO2), demographics
  (AO3), email/purchase behavior (AO4), or the all-variable model (AO5).

## AO1: Data Wrangling & Exploratory Analysis

```{r}
#| label: ao1-wrangle
#| fig-width: 10
#| fig-height: 4.8

# Focused predictor set for AO1
ao1_data <- campaign_data |>
  select(
    AdSpend, ClickThroughRate, WebsiteVisits,
    PagesPerVisit, TimeOnSite, Conversion
  ) |>
  drop_na()

# Compare selected numeric predictors by conversion outcome
p_ao1_spend <- ggplot(ao1_data, aes(Conversion, AdSpend, fill = Conversion)) +
  geom_boxplot(show.legend = FALSE, alpha = 0.8) +
  labs(title = "Advertising Spend by Conversion", x = NULL, y = "Ad Spend")

p_ao1_time <- ggplot(ao1_data, aes(Conversion, TimeOnSite, fill = Conversion)) +
  geom_boxplot(show.legend = FALSE, alpha = 0.8) +
  labs(title = "Time on Site by Conversion", x = NULL, y = "Time on Site")

p_ao1_spend + p_ao1_time
```

- The outcome remains strongly imbalanced: about
  **`r scales::percent(mean(ao1_data$Conversion == "Yes"), accuracy = 0.1)`**
  of customers converted.
- The exploratory plots test whether converted customers tend to show
  different levels of marketing investment exposure and on-site
  engagement.
- Because raw group differences may overlap substantially,
  machine-learning models are used to evaluate their **combined**
  predictive value.

## AO1: Predictor Relationships

```{r}
#| label: ao1-correlations
#| fig-width: 9
#| fig-height: 5

# Point-biserial-style correlations by coding Conversion as 0/1
# (used only as an exploratory summary, not as causal evidence)
ao1_corr <- ao1_data |>
  mutate(Conversion01 = if_else(Conversion == "Yes", 1, 0)) |>
  select(-Conversion) |>
  cor(use = "complete.obs") |>
  as.data.frame() |>
  rownames_to_column("Predictor") |>
  select(Predictor, Conversion01) |>
  filter(Predictor != "Conversion01") |>
  arrange(desc(abs(Conversion01)))

ggplot(ao1_corr, aes(x = reorder(Predictor, Conversion01), y = Conversion01)) +
  geom_col(fill = "#2e75b6") +
  coord_flip() +
  labs(
    title = "Exploratory Association with Conversion",
    x = NULL, y = "Correlation with Conversion (0/1)"
  )
```

- These associations are descriptive and should **not** be interpreted
  as causal effects.
- In this dataset, `AdSpend`, `ClickThroughRate`, and `TimeOnSite` show
  useful univariate signals for conversion, while the model tests
  whether combining all five predictors improves discrimination.

## AO1: Machine Learning Methods

::: panel-tabset
### Logistic Regression

- Interpretable classification baseline
- Estimates the direction of each predictor's relationship with
  conversion while holding the others constant
- Numeric predictors are normalized before fitting so coefficient
  magnitudes are more comparable

### Decision Tree

- Captures non-linear thresholds and interactions
- Easy to explain visually
- Complexity is tuned with cross-validation to reduce overfitting

### Random Forest

- Ensemble of many classification trees
- Captures non-linear patterns and interactions more flexibly
- Permutation importance is used to rank the five predictors
:::

**Primary evaluation metric:** ROC AUC, because accuracy is inflated by
the high baseline conversion rate.

## AO1: Model Fitting

```{r}
#| label: ao1-fit
#| warning: false
#| message: false

set.seed(2026)

# 80/20 stratified split
ao1_split <- initial_split(ao1_data, prop = 0.80, strata = Conversion)
ao1_train <- training(ao1_split)
ao1_test  <- testing(ao1_split)
ao1_folds <- vfold_cv(ao1_train, v = 5, strata = Conversion)

# Leakage-safe preprocessing: estimate scaling from training data only
ao1_recipe <- recipe(Conversion ~ ., data = ao1_train) |>
  step_zv(all_predictors()) |>
  step_normalize(all_numeric_predictors())

# Model specifications
ao1_logit_spec <- logistic_reg() |>
  set_engine("glm") |>
  set_mode("classification")

ao1_tree_spec <- decision_tree(
  cost_complexity = tune(), tree_depth = tune(), min_n = tune()
) |>
  set_engine("rpart") |>
  set_mode("classification")

ao1_rf_spec <- rand_forest(
  trees = 500, mtry = tune(), min_n = tune()
) |>
  set_engine("ranger", importance = "permutation", probability = TRUE) |>
  set_mode("classification")

# Workflows
ao1_logit_wf <- workflow() |> add_recipe(ao1_recipe) |> add_model(ao1_logit_spec)
ao1_tree_wf  <- workflow() |> add_recipe(ao1_recipe) |> add_model(ao1_tree_spec)
ao1_rf_wf    <- workflow() |> add_recipe(ao1_recipe) |> add_model(ao1_rf_spec)

# Tune flexible models by ROC AUC
ao1_tree_res <- tune_grid(
  ao1_tree_wf, resamples = ao1_folds, grid = 12,
  metrics = metric_set(roc_auc)
)

ao1_rf_res <- tune_grid(
  ao1_rf_wf, resamples = ao1_folds, grid = 12,
  metrics = metric_set(roc_auc)
)

# Final training fits
ao1_logit_fit <- fit(ao1_logit_wf, data = ao1_train)
ao1_tree_fit <- finalize_workflow(
  ao1_tree_wf, select_best(ao1_tree_res, metric = "roc_auc")
) |> fit(data = ao1_train)
ao1_rf_fit <- finalize_workflow(
  ao1_rf_wf, select_best(ao1_rf_res, metric = "roc_auc")
) |> fit(data = ao1_train)
```

- **Split:** 80% training / 20% testing, stratified by conversion
- **Cross-validation:** 5 folds on the training set
- **Preprocessing:** zero-variance removal + normalization of numeric
  predictors
- **Tuning:** Decision Tree and Random Forest tuned using ROC AUC

## AO1: Prediction & Model Evaluation

```{r}
#| label: ao1-eval
#| fig-width: 8.5
#| fig-height: 4.8

make_ao1_preds <- function(fit_obj, model_name) {
  bind_cols(
    ao1_test,
    predict(fit_obj, new_data = ao1_test, type = "prob"),
    predict(fit_obj, new_data = ao1_test, type = "class")
  ) |>
    mutate(model = model_name)
}

ao1_results <- bind_rows(
  make_ao1_preds(ao1_logit_fit, "Logistic Regression"),
  make_ao1_preds(ao1_tree_fit, "Decision Tree"),
  make_ao1_preds(ao1_rf_fit, "Random Forest")
)

ao1_metrics <- ao1_results |>
  group_by(model) |>
  summarise(
    Accuracy = accuracy_vec(Conversion, .pred_class),
    ROC_AUC = roc_auc_vec(Conversion, .pred_Yes, event_level = "second"),
    Sensitivity = sens_vec(Conversion, .pred_class, event_level = "second"),
    Specificity = spec_vec(Conversion, .pred_class, event_level = "second"),
    .groups = "drop"
  ) |>
  mutate(across(where(is.numeric), ~ round(.x, 3)))

ao1_metrics

ao1_results |>
  group_by(model) |>
  roc_curve(Conversion, .pred_Yes, event_level = "second") |>
  autoplot() +
  labs(title = "AO1 ROC Curves — Held-Out Test Set")
```

- The majority-class baseline accuracy is about
  **`r scales::percent(mean(ao1_test$Conversion == "Yes"), accuracy = 0.1)`**,
  so accuracy alone is not sufficient.
- ROC AUC evaluates whether the models correctly **rank higher-risk and
  lower-risk customers** across classification thresholds.
- AUC materially above 0.50 indicates that marketing investment and
  on-site engagement contain predictive signal beyond simply guessing
  the majority class.

## AO1: Interpretation — Logistic Regression

```{r}
#| label: ao1-logit-interpret
#| fig-width: 8.5
#| fig-height: 4.8

# Because predictors were standardized, each odds ratio represents
# approximately a one-standard-deviation increase in that predictor.
ao1_odds <- ao1_logit_fit |>
  extract_fit_parsnip() |>
  tidy(exponentiate = TRUE, conf.int = TRUE) |>
  filter(term != "(Intercept)") |>
  mutate(term = forcats::fct_reorder(term, estimate))

ggplot(ao1_odds, aes(x = estimate, y = term)) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey50") +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2) +
  geom_point(size = 3, color = "#1f3864") +
  labs(
    title = "Logistic Regression — Standardized Odds Ratios",
    x = "Odds Ratio (95% CI)", y = NULL
  )
```

- Odds ratios above 1 indicate higher conversion odds as the predictor
  increases; values below 1 indicate lower odds.
- Standardization makes the five numeric predictors more comparable on
  the same plot.
- This interpretation describes **predictive association**, not a causal
  return on advertising spend.

## AO1: Interpretation — Random Forest Importance & PDP

```{r}
#| label: ao1-rf-interpret
#| fig-width: 10
#| fig-height: 4.8

p_ao1_vip <- ao1_rf_fit |>
  extract_fit_parsnip() |>
  vip(num_features = 5) +
  labs(title = "Random Forest Variable Importance")

# Manual partial dependence for AdSpend:
# replace AdSpend for every test observation across a grid, predict,
# then average predicted conversion probability.
ao1_spend_grid <- seq(
  quantile(ao1_test$AdSpend, 0.05),
  quantile(ao1_test$AdSpend, 0.95),
  length.out = 30
)

ao1_pdp_spend <- map_dfr(ao1_spend_grid, function(x) {
  new_dat <- ao1_test |> mutate(AdSpend = x)
  tibble(
    AdSpend = x,
    PredictedConversion = mean(
      predict(ao1_rf_fit, new_data = new_dat, type = "prob")$.pred_Yes
    )
  )
})

p_ao1_pdp <- ggplot(ao1_pdp_spend, aes(AdSpend, PredictedConversion)) +
  geom_line(linewidth = 1.2, color = "#2e75b6") +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Partial Dependence of Conversion on Ad Spend",
    x = "Ad Spend", y = "Average Predicted Conversion Probability"
  )

p_ao1_vip + p_ao1_pdp
```

- **Variable importance** identifies which investment/engagement signals
  contribute most to the Random Forest's predictions.
- The **partial dependence plot (PDP)** shows the model's average
  predicted conversion probability as `AdSpend` changes while the
  observed distribution of the other predictors is retained.
- A nonlinear or flattening PDP would suggest that the relationship is
  more complex than “spend more = convert more.”

## AO1: Summary Findings

::: incremental
- **Focused predictive signal:** Advertising spend and on-site
  engagement variables provide meaningful information for distinguishing
  converters from non-converters, but they do not perfectly separate the
  two groups.
- **Use ROC AUC, not accuracy alone:** The dataset's approximately
  **87.7% conversion rate** makes majority-class accuracy deceptively
  high.
- **Model comparison matters:** Logistic Regression provides an
  interpretable baseline, while Decision Tree and Random Forest test
  whether nonlinear thresholds and interactions improve discrimination.
- **Interpretability:** Standardized odds ratios, Random Forest variable
  importance, and the AdSpend PDP show which signals matter and how
  predicted conversion changes across spending levels.
- **Business implication:** Use advertising spend together with
  engagement signals when prioritizing customers or evaluating
  campaigns; avoid assuming that higher spend by itself guarantees
  higher conversion.
- **Caution:** These results are predictive associations from an
  observational dataset and should not be interpreted as proof that
  increasing advertising spend *causes* conversion.
:::

<!-- =================================================================== -->

<!-- AO2 —The impact of marketing channels and campaign types on customer conversion -->

<!-- =================================================================== -->

# Analytics Objective 2 — *Jungmin Woo*

## AO2: Campaign Performance {.smaller}

> RO2: Analyze the impact of marketing channels and campaign types on
> customer conversion.

- **IV (predictors):** `CampaignChannel`, `CampaignType` (both
  categorical)
- **DV (target):** `Conversion` (binary — Yes / No)
- **Problem type:** Classification
- Only these two categorical variables are used as predictors, so this
  AO isolates the effect of *channel* and *campaign type* on conversion,
  independent of demographic or on-site behavior variables

## AO2: Machine Learning Methods to be Used

::: panel-tabset
### Regression-Focused Methods

- Not applicable (outcome is categorical)

### Classification-Focused Methods

- Logistic Regression
- Decision Tree (classification)

### Ensembles

- Random Forest (classification)
:::

## AO2: Data Wrangling & Visualization

```{r}
#| label: ao2-wrangle

# Missing-value check on the relevant columns
campaign_data |>
  select(CampaignChannel, CampaignType, Conversion) |>
  summarise(across(everything(), ~ sum(is.na(.))))

# Baseline conversion rate by Channel x Type
ao2_baseline <- campaign_data |>
  group_by(CampaignChannel, CampaignType) |>
  summarise(
    ConversionRate = mean(Conversion == "Yes"),
    N = n(),
    .groups = "drop"
  ) |>
  arrange(desc(ConversionRate))

ao2_baseline
```

```{r}
#| label: ao2-viz
#| fig-width: 9
#| fig-height: 5

ggplot(ao2_baseline, aes(x = CampaignChannel, y = ConversionRate, fill = CampaignType)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Conversion Rate by Channel, Segmented by Campaign Type",
    x = "Campaign Channel", y = "Conversion Rate", fill = "Campaign Type"
  ) +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

- No missing values in `CampaignChannel`, `CampaignType`, or
  `Conversion`
- The bar chart shows very little spread **across channels** within each
  campaign type (bars of the same color are roughly the same height),
  but a clear gap **across campaign types**:
  `CampaignType == "Conversion"` sits noticeably higher (\~92–94%) than
  `Awareness`, `Consideration`, or `Retention` (\~84–88%) in every
  channel
- This suggests campaign *type* may matter more than campaign *channel*
  for conversion — tested formally below

## AO2: Model Fitting

```{r}
#| label: ao2-fit

set.seed(2026)

ao2_data <- campaign_data |>
  select(CampaignChannel, CampaignType, Conversion)

# --- Data splitting ---
ao2_split <- initial_split(ao2_data, prop = 0.8, strata = Conversion)
ao2_train <- training(ao2_split)
ao2_test  <- testing(ao2_split)
ao2_folds <- vfold_cv(ao2_train, v = 5, strata = Conversion)

# --- Recipe ---
ao2_recipe <- recipe(Conversion ~ CampaignChannel + CampaignType, data = ao2_train) |>
  step_dummy(all_nominal_predictors()) |>
  step_zv(all_predictors())

# --- Model specifications ---
ao2_spec_glm <- logistic_reg() |>
  set_engine("glm") |>
  set_mode("classification")

ao2_spec_tree <- decision_tree(cost_complexity = tune(), tree_depth = tune()) |>
  set_engine("rpart") |>
  set_mode("classification")

ao2_spec_rf <- rand_forest(trees = 500, min_n = tune()) |>
  set_engine("ranger", importance = "permutation") |>
  set_mode("classification")

# --- Workflows ---
ao2_wf_glm  <- workflow() |> add_recipe(ao2_recipe) |> add_model(ao2_spec_glm)
ao2_wf_tree <- workflow() |> add_recipe(ao2_recipe) |> add_model(ao2_spec_tree)
ao2_wf_rf   <- workflow() |> add_recipe(ao2_recipe) |> add_model(ao2_spec_rf)

# --- Tuning ---
ao2_tree_res <- tune_grid(ao2_wf_tree, resamples = ao2_folds, grid = 5,
                           metrics = metric_set(roc_auc))
ao2_rf_res   <- tune_grid(ao2_wf_rf, resamples = ao2_folds, grid = 5,
                           metrics = metric_set(roc_auc))

# --- Finalize + fit ---
ao2_fit_glm  <- fit(ao2_wf_glm, data = ao2_train)
ao2_fit_tree <- finalize_workflow(ao2_wf_tree, select_best(ao2_tree_res, metric = "roc_auc")) |>
  fit(data = ao2_train)
ao2_fit_rf   <- finalize_workflow(ao2_wf_rf, select_best(ao2_rf_res, metric = "roc_auc")) |>
  fit(data = ao2_train)
```

## AO2: Prediction & Model Evaluation

```{r}
#| label: ao2-eval

ao2_class_metrics <- metric_set(accuracy, roc_auc, f_meas)

ao2_results <- bind_rows(
  augment(ao2_fit_glm,  new_data = ao2_test) |> mutate(model = "Logistic Regression"),
  augment(ao2_fit_tree, new_data = ao2_test) |> mutate(model = "Decision Tree"),
  augment(ao2_fit_rf,   new_data = ao2_test) |> mutate(model = "Random Forest")
)

ao2_metrics <- ao2_results |>
  group_by(model) |>
  ao2_class_metrics(truth = Conversion, estimate = .pred_class, .pred_Yes, event_level = "second")

ao2_metrics
```

- All three models land at essentially the same accuracy (\~87.6%),
  which matches the overall base rate of `Conversion == "Yes"` in the
  data — the models are not beating a "always predict Yes" baseline on
  accuracy alone
- ROC AUC is low (\~0.53–0.54, just above the 0.50 random-guess line),
  meaning `CampaignChannel` and `CampaignType` alone have only weak
  discriminative power for *individual-level* conversion, even though
  the group-level rates in the bar chart differ by type
- This is a common pattern: a variable can show a real, statistically
  significant *group-level* effect while still being a weak
  *individual-level* predictor, because most of the variation in who
  converts is driven by other factors (behavioral, demographic) not
  included in this AO by design

## AO2: Interpretation

```{r}
#| label: ao2-interpret
#| fig-width: 8
#| fig-height: 4.5

# Association test: does Channel matter? Does Type matter?
chisq.test(table(campaign_data$CampaignChannel, campaign_data$Conversion))
chisq.test(table(campaign_data$CampaignType, campaign_data$Conversion))

# Logistic regression coefficients (log-odds effect of each channel/type)
ao2_fit_glm |> tidy() |> arrange(p.value)

# Variable importance from Random Forest
ao2_fit_rf |> extract_fit_parsnip() |> vip(num_features = 10)
```

- The chi-square test for `CampaignChannel` is **not significant** (χ² ≈
  2.78, p ≈ 0.59) — channel choice alone shows no reliable association
  with conversion
- The chi-square test for `CampaignType` **is significant** (χ² ≈ 84.5,
  p \< 0.001) — campaign type is meaningfully associated with
  conversion, driven mainly by the `"Conversion"` type having a
  substantially higher rate (\~93%) than
  `Awareness`/`Consideration`/`Retention` (\~84–88%)
- Random Forest variable importance should echo this: dummy variables
  for `CampaignType` should rank above `CampaignChannel` dummies

## AO2: Summary Findings

::: incremental
- **Campaign type** has a statistically significant relationship with
  conversion; **campaign channel** does not, at least on its own
- The higher conversion rate for `CampaignType == "Conversion"`
  campaigns is expected by design (these campaigns are explicitly built
  to drive conversion) but confirms the labeling is consistent with
  actual outcomes
- Despite the significant group-level association, channel + type alone
  give weak individual-level predictive power (ROC AUC ≈ 0.53) — they
  are not sufficient by themselves to identify which specific customers
  will convert
- **Business implication:** channel selection appears interchangeable
  for conversion purposes in this data, so budget allocation decisions
  should weigh cost-per-channel and other KPIs rather than assuming any
  one channel converts better; campaign *type* mix (more bottom-funnel
  "Conversion"-type campaigns) is the lever more strongly tied to
  conversion outcomes
:::

<!-- =================================================================== -->

<!-- AO3 — Customer Demographics and Conversion                            -->

<!-- =================================================================== -->

# Analytics Objective 3 — *Grace Sen*

```{r}
#| label: ao3-hidden-setup
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(tidymodels)
library(ranger)
library(scales)

tidymodels_prefer()
set.seed(6540)

cpp_green <- "#1E4D2B"
cpp_gold  <- "#FFB81C"
cpp_gray  <- "#5C6670"

theme_set(
  theme_minimal(base_size = 17) +
    theme(
      plot.title.position = "plot",
      plot.title = element_text(face = "bold", color = cpp_green),
      legend.position = "bottom",
      panel.grid.minor = element_blank()
    )
)

data_path <- "digital_marketing_campaign_dataset.csv"

marketing_raw <- read_csv(data_path, show_col_types = FALSE) |>
  rename_with(~ tolower(gsub("[^A-Za-z0-9]+", "_", .x)))

ao3 <- marketing_raw |>
  transmute(
    age = age,
    gender = factor(gender),
    income = income,
    conversion = factor(
      conversion,
      levels = c(1, 0),
      labels = c("Converted", "Not converted")
    )
  )

outcome_summary <- ao3 |>
  count(conversion) |>
  mutate(proportion = n / sum(n))

gender_rates <- ao3 |>
  group_by(gender) |>
  summarise(
    customers = n(),
    conversion_rate = mean(conversion == "Converted"),
    .groups = "drop"
  )

set.seed(6540)
ao3_split <- initial_split(ao3, prop = 0.75, strata = conversion)
ao3_train <- training(ao3_split)
ao3_test  <- testing(ao3_split)

ao3_recipe <- recipe(conversion ~ age + gender + income, data = ao3_train) |>
  step_unknown(all_nominal_predictors()) |>
  step_novel(all_nominal_predictors()) |>
  step_dummy(all_nominal_predictors(), one_hot = FALSE) |>
  step_zv(all_predictors()) |>
  step_normalize(all_numeric_predictors())

log_spec <- logistic_reg() |>
  set_engine("glm") |>
  set_mode("classification")

log_workflow <- workflow() |>
  add_recipe(ao3_recipe) |>
  add_model(log_spec)

log_fit <- fit(log_workflow, data = ao3_train)

set.seed(6540)
ao3_folds <- vfold_cv(ao3_train, v = 5, strata = conversion)

rf_spec <- rand_forest(
  trees = 500,
  mtry = tune(),
  min_n = tune()
) |>
  set_engine("ranger", probability = TRUE, importance = "permutation") |>
  set_mode("classification")

rf_workflow <- workflow() |>
  add_recipe(ao3_recipe) |>
  add_model(rf_spec)

rf_grid <- grid_regular(
  mtry(range = c(1L, 3L)),
  min_n(range = c(5L, 30L)),
  levels = c(mtry = 3, min_n = 4)
)

set.seed(6540)
rf_tuned <- tune_grid(
  rf_workflow,
  resamples = ao3_folds,
  grid = rf_grid,
  metrics = metric_set(roc_auc, pr_auc, bal_accuracy),
  control = control_grid(save_pred = TRUE)
)

best_rf <- select_best(rf_tuned, metric = "roc_auc")
final_rf_workflow <- finalize_workflow(rf_workflow, best_rf)
rf_fit <- fit(final_rf_workflow, data = ao3_train)

predict_with_probabilities <- function(fitted_workflow, new_data, model_name) {
  bind_cols(
    new_data |> select(conversion),
    predict(fitted_workflow, new_data, type = "class"),
    predict(fitted_workflow, new_data, type = "prob")
  ) |>
    mutate(model = model_name)
}

log_predictions <- predict_with_probabilities(
  log_fit, ao3_test, "Logistic regression"
)
rf_predictions <- predict_with_probabilities(
  rf_fit, ao3_test, "Random forest"
)

baseline_predictions <- ao3_test |>
  transmute(
    conversion,
    .pred_class = factor("Converted", levels = levels(conversion)),
    .pred_Converted = mean(ao3_train$conversion == "Converted"),
    .pred_Not.converted = 1 - .pred_Converted,
    model = "Majority baseline"
  )

all_predictions <- bind_rows(
  baseline_predictions,
  log_predictions,
  rf_predictions
)

classification_metrics <- metric_set(
  accuracy, bal_accuracy, sens, spec, precision, recall
)

class_results <- all_predictions |>
  group_by(model) |>
  classification_metrics(truth = conversion, estimate = .pred_class)

probability_results <- all_predictions |>
  group_by(model) |>
  metric_set(roc_auc, pr_auc)(
    truth = conversion,
    .pred_Converted,
    event_level = "first"
  )

model_metrics <- bind_rows(class_results, probability_results) |>
  select(model, .metric, .estimate) |>
  pivot_wider(names_from = .metric, values_from = .estimate)

best_model_row <- model_metrics |>
  filter(model != "Majority baseline") |>
  slice_max(roc_auc, n = 1, with_ties = FALSE)

log_odds_ratios <- extract_fit_parsnip(log_fit) |>
  tidy() |>
  filter(term != "(Intercept)") |>
  mutate(
    odds_ratio = exp(estimate),
    lower_95 = exp(estimate - 1.96 * std.error),
    upper_95 = exp(estimate + 1.96 * std.error)
  ) |>
  select(term, odds_ratio, lower_95, upper_95, p.value)

rf_engine <- extract_fit_engine(rf_fit)
rf_importance <- enframe(
  rf_engine$variable.importance,
  name = "feature",
  value = "importance"
) |>
  arrange(desc(importance))
```

## Do demographics help identify customers who convert? {background-color="#1E4D2B"}

### Analytics Objective 3

Examine whether **age, gender, and income** are associated with—and
useful for predicting—customer conversion.

::: objective-line
**Predictors:** Age · Gender · Income\
**Outcome:** Conversion (binary classification)
:::

::: notes
My analytics objective asks whether customer demographics help explain
and predict conversion. I use age, gender, and income as predictors and
conversion as the binary outcome. The analysis compares an interpretable
logistic regression with a nonlinear ensemble model.
:::

## AO3: Data Wrangling & Visualization — Sample and Outcome

:::::: columns
::: {.column width="48%"}
```{r}
#| fig-width: 7
#| fig-height: 4.4
ggplot(outcome_summary, aes(x = conversion, y = proportion, fill = conversion)) +
  geom_col(width = 0.62, show.legend = FALSE) +
  geom_text(
    aes(label = percent(proportion, accuracy = 0.1)),
    vjust = -0.35,
    size = 6
  ) +
  scale_fill_manual(values = c(cpp_green, cpp_gold)) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  labs(x = NULL, y = "Share of customers")
```
:::

:::: {.column width="48%"}
- **`r (nrow(ao3))` customers**
- **`r sum(is.na(ao3))` missing values** in AO3 variables
- Conversion rate:
  `r scales::percent(mean(ao3$conversion == "Converted"), accuracy = 0.1)`

::: key-message
Accuracy alone is misleading: predicting “Converted” for everyone
already produces high accuracy.
:::

**Primary metrics:** ROC AUC, PR AUC, balanced accuracy, sensitivity,
and specificity.
::::
::::::

::: notes
The dataset contains 8,000 customers and no missing values in the four
variables used here. Conversion is highly imbalanced. Because almost
nine out of ten customers converted, accuracy can look strong even when
a model does not separate the two classes. I therefore emphasize
discrimination and class-balanced metrics.
:::

## AO3: Data Wrangling & Visualization — Income and Gender

::::: columns
::: {.column width="50%"}
```{r}
#| fig-width: 6.8
#| fig-height: 4.7
ggplot(ao3, aes(x = conversion, y = income, fill = conversion)) +
  geom_boxplot(width = 0.62, alpha = 0.88, outlier.alpha = 0.18) +
  scale_fill_manual(values = c(cpp_green, cpp_gold), guide = "none") +
  scale_y_continuous(labels = dollar) +
  labs(title = "Income distributions overlap", x = NULL, y = "Annual income")
```
:::

::: {.column width="50%"}
```{r}
#| fig-width: 6.8
#| fig-height: 4.7
ggplot(gender_rates, aes(x = gender, y = conversion_rate, fill = gender)) +
  geom_col(width = 0.62, show.legend = FALSE) +
  geom_text(
    aes(label = percent(conversion_rate, accuracy = 0.01)),
    vjust = -0.35,
    size = 5.5
  ) +
  scale_fill_manual(values = c(cpp_green, cpp_gold)) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  labs(title = "Gender rates are nearly identical", x = NULL, y = "Conversion rate")
```
:::
:::::

::: takeaway
Neither income nor gender appears to distinguish converters from
non-converters on its own.
:::

::: notes
The descriptive patterns already suggest weak demographic effects.
Income medians and distributions substantially overlap across outcomes,
while conversion rates are nearly equal across gender groups. These
plots are descriptive, so the models next test whether the variables
work better jointly.
:::

## AO3: Data Wrangling & Visualization — Age

```{r}
#| fig-width: 10.5
#| fig-height: 5.3
ggplot(ao3, aes(x = age, color = conversion)) +
  geom_density(linewidth = 1.5, adjust = 1.1) +
  scale_color_manual(values = c(cpp_green, cpp_gold)) +
  labs(x = "Age", y = "Density", color = NULL)
```

::: takeaway
Age provides little visible univariate discrimination across nearly the
entire range.
:::

::: notes
The age density curves overlap across almost the full distribution.
Taken together, the exploratory results provide little evidence that any
single demographic variable strongly separates the outcome classes.
:::

## AO3: Machine Learning Methods & Model Fitting {.smaller}

:::::: columns
::: {.column width="46%"}
### Logistic regression

- Interpretable adjusted associations
- Standardized age and income
- Odds ratios with 95% confidence intervals

### Random forest

- Captures nonlinearities and interactions
- 500 trees
- Five-fold stratified cross-validation
- Tuned `mtry` and minimum node size
:::

:::: {.column width="50%"}
### Leakage-safe evaluation

1.  Stratified **75/25 train–test split**
2.  Training-only preprocessing recipe
3.  Dummy-code gender; normalize numeric predictors
4.  Tune the forest within training folds
5.  Evaluate once on the untouched test set

::: key-message
The majority-class prediction serves as the benchmark.
:::
::::
::::::

::: notes
Logistic regression provides interpretable adjusted effects. Random
forest tests whether nonlinear patterns or interactions add predictive
value. The split is stratified, all preprocessing is learned on the
training data only, and the test data remains untouched until final
evaluation.
:::

## AO3: Prediction & Model Evaluation

:::::: columns
::: {.column width="60%"}
```{r}
#| fig-width: 8
#| fig-height: 5
model_metrics |>
  filter(model != "Majority baseline") |>
  select(model, roc_auc, bal_accuracy) |>
  pivot_longer(-model, names_to = "metric", values_to = "score") |>
  mutate(metric = recode(
    metric,
    roc_auc = "ROC AUC",
    bal_accuracy = "Balanced accuracy"
  )) |>
  ggplot(aes(x = metric, y = score, fill = model)) +
  geom_col(position = position_dodge(width = 0.75), width = 0.64) +
  geom_hline(yintercept = 0.50, linetype = "dashed", color = cpp_gray) +
  geom_text(
    aes(label = number(score, accuracy = 0.001)),
    position = position_dodge(width = 0.75),
    vjust = -0.35,
    size = 5
  ) +
  scale_fill_manual(values = c(cpp_green, cpp_gold)) +
  scale_y_continuous(
    limits = c(0, max(0.70, max(model_metrics$roc_auc, na.rm = TRUE) + 0.08))
  ) +
  labs(x = NULL, y = "Test-set score", fill = NULL)
```
:::

:::: {.column width="36%"}
### Held-out conclusion

Better-performing model: **`r best_model_row$model`**

ROC AUC: `r scales::number(best_model_row$roc_auc, accuracy = 0.001)`

Balanced accuracy:
`r scales::number(best_model_row$bal_accuracy, accuracy = 0.001)`

::: key-message
Scores near 0.50 indicate little ability to rank converters above
non-converters.
:::
::::
::::::

::: notes
On the held-out test set, the best demographic model has an ROC AUC and
balanced accuracy near 0.50. That is approximately chance-level
performance. High raw accuracy would not change this conclusion because
the converted class dominates the sample.
:::

## AO3: Interpretation — Logistic Regression

::::: columns
::: {.column width="62%"}
```{r}
#| fig-width: 8
#| fig-height: 5
ggplot(log_odds_ratios, aes(x = odds_ratio, y = reorder(term, odds_ratio))) +
  geom_vline(xintercept = 1, linetype = "dashed", color = cpp_gray) +
  geom_errorbarh(
    aes(xmin = lower_95, xmax = upper_95),
    height = 0.16,
    color = cpp_green,
    linewidth = 1
  ) +
  geom_point(size = 4, color = cpp_green) +
  labs(x = "Odds ratio with 95% CI", y = NULL)
```
:::

::: {.column width="34%"}
- Odds ratios near **1.00** indicate weak adjusted associations.
- Intervals crossing **1.00** indicate limited evidence after
  controlling for the other demographics.
- Association does not imply causation.
:::
:::::

::: notes
The logistic regression provides adjusted effects. Age and income are
standardized, so each odds ratio represents a one-standard-deviation
increase. Effects close to one, particularly with confidence intervals
crossing one, support the same substantive conclusion as the held-out
model evaluation.
:::

## AO3: Interpretation — Random Forest

:::::: columns
::: {.column width="62%"}
```{r}
#| fig-width: 8
#| fig-height: 5
ggplot(rf_importance, aes(x = importance, y = reorder(feature, importance))) +
  geom_col(fill = cpp_green, width = 0.64) +
  labs(x = "Permutation importance", y = NULL)
```
:::

:::: {.column width="34%"}
Permutation importance ranks predictors **within the fitted forest**.

::: key-message
A weak model can still rank weak predictors. Importance is relative and
does not establish a business driver or causal effect.
:::
::::
::::::

::: notes
The random forest still produces a ranking because permutation
importance is relative. We should not describe the top-ranked
demographic as a strong driver when the entire model performs near
chance. Variable importance also does not establish causality.
:::

## AO3: Summary Findings

::::: columns
::: {.column width="48%"}
### What AO3 found

- Demographic distributions overlap substantially.
- Both models showed weak test-set discrimination.
- Demographics alone are insufficient for targeting.
:::

::: {.column width="48%"}
### Business implication

- Prioritize behavioral and engagement signals.
- Use demographics for segmentation and fairness checks.
- Validate the final model on external data.
:::
:::::

**Takeaway:** Customer behavior is more promising than demographics for
predicting conversion.

::: notes
The overall conclusion is that demographics alone do not meaningfully
distinguish converters from non-converters. The business should
prioritize engagement variables such as website visits, time on site,
email activity, prior purchases, and campaign interactions. Demographics
may remain useful for segmentation and fairness monitoring, but not as
the primary targeting inputs.
:::

<!-- =================================================================== -->

<!-- AO4 —  Customer Interaction, Purchase Behavior, and Conversion                           -->

<!-- =================================================================== -->

# Analytics Objective 4 — *Sandy Zhu*

## AO4: Customer Interaction, Purchase Behavior, and Conversion

RO4: How do email engagement (EmailOpens and EmailClicks) and previous
purchases affect customer conversion, and which factor is the most
important for predicting conversion?

- **Target variables:** `ConversionRate`, `Conversion` (No / Yes)
- **Independent variables:** `EmailOpens`, `EmailClicks`,
  `PreviousPurchases`
- **Problem type:** Regression and binary classification

------------------------------------------------------------------------

- **Business question:** How do email engagement and previous purchases
  relate to customer conversion?
- **Analytical focus:** Compare models and identify which customer
  behavior is most important for predicting conversion.

## AO4: Machine Learning Methods to be Used

### Regression-Focused Method

- **Linear Regression** — predicts `ConversionRate` as a continuous
  marketing outcome.

### Classification-Focused Method

- **Logistic Regression** — predicts whether a customer converts (`Yes`
  / `No`).

------------------------------------------------------------------------

### Ensemble Method

- **Random Forest** — captures nonlinear patterns and identifies
  important behavioral predictors.

## AO4: Data Wrangling & Visualization

```{r}
#| label: ao4-wrangle
#| fig-width: 10
#| fig-height: 4.5

# Keep only variables required by RO4
ao4_data <- raw_data |>
  select(
    EmailOpens,
    EmailClicks,
    PreviousPurchases,
    ConversionRate,
    Conversion
  ) |>
  drop_na() |>
  mutate(
    Conversion = factor(
      Conversion,
      levels = c(0, 1),
      labels = c("No", "Yes")
    )
  )

# Summary statistics by conversion status
ao4_summary <- ao4_data |>
  group_by(Conversion) |>
  summarise(
    n = n(),
    mean_opens = mean(EmailOpens),
    mean_clicks = mean(EmailClicks),
    mean_purchases = mean(PreviousPurchases),
    .groups = "drop"
  )

# Conversion distribution
ao4_conversion <- ao4_data |>
  count(Conversion) |>
  mutate(
    percent = n / sum(n)
  )

p_ao4_conversion <- ggplot(
  ao4_conversion,
  aes(x = Conversion, y = percent)
) +
  geom_col(fill = "#2e75b6") +
  geom_text(
    aes(label = scales::percent(percent, accuracy = 0.1)),
    vjust = -0.4,
    size = 4
  ) +
  scale_y_continuous(
    labels = scales::percent,
    limits = c(0, 1)
  ) +
  labs(
    title = "Customer Conversion Distribution",
    x = "Conversion Status",
    y = "Percentage of Customers"
  )

# Behavioral comparison by conversion status
ao4_long <- ao4_data |>
  select(Conversion, EmailOpens, EmailClicks, PreviousPurchases) |>
  pivot_longer(
    cols = -Conversion,
    names_to = "Behavior",
    values_to = "Value"
  )

p_ao4_behavior <- ggplot(
  ao4_long,
  aes(x = Conversion, y = Value)
) +
  geom_boxplot() +
  facet_wrap(~ Behavior, scales = "free_y") +
  labs(
    title = "Customer Behavior by Conversion Status",
    x = "Conversion Status",
    y = NULL
  )

patchwork::wrap_plots(
  p_ao4_conversion,
  p_ao4_behavior,
  ncol = 2
)
```

- The dataset contains **8,000 customers**, with no missing values in
  the variables used for RO4.
- Approximately **87.7%** of customers converted, indicating substantial
  class imbalance in the binary outcome.
- Customers who converted generally show higher `EmailOpens`,
  `EmailClicks`, and `PreviousPurchases` than non-converters.
- These descriptive patterns suggest that customer interaction and prior
  purchasing behavior may contain useful information for predicting
  conversion.

## AO4: Customer Behavior × Conversion Pattern

```{r}
#| label: ao4-behavior-pattern
#| fig-width: 10
#| fig-height: 4.5

# Reshape behavioral variables for comparison
ao4_behavior <- ao4_data |>
  select(Conversion, EmailOpens, EmailClicks, PreviousPurchases) |>
  pivot_longer(
    cols = c(EmailOpens, EmailClicks, PreviousPurchases),
    names_to = "Behavior",
    values_to = "Value"
  )

ggplot(ao4_behavior,
       aes(x = Conversion, y = Value, fill = Conversion)) +
  geom_boxplot(alpha = 0.8, show.legend = FALSE) +
  facet_wrap(
    ~ Behavior,
    scales = "free_y",
    nrow = 1
  ) +
  labs(
    title = "Customer Behavior by Conversion Status",
    x = "Conversion Status",
    y = NULL
  ) +
  theme_minimal()
```

- Converted customers show **higher email engagement** (median opens:
  **10 vs. 6**; clicks: **5 vs. 3**).
- They also have **more previous purchases**, suggesting stronger
  engagement is associated with conversion.

## AO4: Model Fitting

```{r}
#| label: ao4-fit

set.seed(2026)

# 80/20 stratified split
ao4_split <- initial_split(
  ao4_data,
  prop = 0.80,
  strata = Conversion
)

ao4_train <- training(ao4_split)
ao4_test  <- testing(ao4_split)

# --------------------------------------------------
# Linear Regression: ConversionRate
# --------------------------------------------------

ao4_fit_lm <- workflow() |>
  add_recipe(
    recipe(
      ConversionRate ~ EmailOpens + EmailClicks + PreviousPurchases,
      data = ao4_train
    ) |>
      step_zv(all_predictors()) |>
      step_normalize(all_numeric_predictors())
  ) |>
  add_model(
    linear_reg() |>
      set_engine("lm")
  ) |>
  fit(data = ao4_train)

# --------------------------------------------------
# Classification recipe: Conversion
# --------------------------------------------------

ao4_recipe <- recipe(
  Conversion ~ EmailOpens + EmailClicks + PreviousPurchases,
  data = ao4_train
) |>
  step_zv(all_predictors()) |>
  step_normalize(all_numeric_predictors())

# Logistic Regression
ao4_fit_logit <- workflow() |>
  add_recipe(ao4_recipe) |>
  add_model(
    logistic_reg() |>
      set_engine("glm")
  ) |>
  fit(data = ao4_train)

# Decision Tree
ao4_fit_tree <- workflow() |>
  add_recipe(ao4_recipe) |>
  add_model(
    decision_tree(
      tree_depth = 5,
      min_n = 20
    ) |>
      set_engine("rpart") |>
      set_mode("classification")
  ) |>
  fit(data = ao4_train)

# Random Forest
ao4_fit_rf <- workflow() |>
  add_recipe(ao4_recipe) |>
  add_model(
    rand_forest(
      trees = 500,
      mtry = 2,
      min_n = 10
    ) |>
      set_engine(
        "ranger",
        importance = "permutation",
        probability = TRUE
      ) |>
      set_mode("classification")
  ) |>
  fit(data = ao4_train)
```

- **Split:** 80% training / 20% testing, stratified by `Conversion`
- **Regression model:** Linear Regression predicts `ConversionRate`
- **Classification models:** Logistic Regression, Decision Tree, and
  Random Forest predict `Conversion`
- **Purpose:** compare interpretable linear/classification methods with
  tree-based and ensemble approaches.

## AO4: Prediction & Model Evaluation

```{r}
#| label: ao4-eval
#| fig-width: 8
#| fig-height: 4.5

# ------------------------------------------------------------
# Regression model evaluation
# ------------------------------------------------------------

ao4_reg_results <- bind_cols(
  ao4_test |> select(ConversionRate),
  predict(ao4_fit_lm, new_data = ao4_test)
)

ao4_reg_metrics <- ao4_reg_results |>
  metrics(
    truth = ConversionRate,
    estimate = .pred
  )

ao4_reg_metrics


# ------------------------------------------------------------
# Classification model evaluation
# ------------------------------------------------------------

# Generate class probabilities and predictions
make_ao4_preds <- function(fit_obj, model_name) {
  bind_cols(
    ao4_test,
    predict(fit_obj, new_data = ao4_test, type = "prob"),
    predict(fit_obj, new_data = ao4_test, type = "class")
  ) |>
    mutate(model = model_name)
}

ao4_results <- bind_rows(
  make_ao4_preds(ao4_fit_logit, "Logistic Regression"),
  make_ao4_preds(ao4_fit_tree,  "Decision Tree"),
  make_ao4_preds(ao4_fit_rf,    "Random Forest")
)

# Classification performance
ao4_metrics <- ao4_results |>
  group_by(model) |>
  summarise(
    Accuracy = accuracy_vec(
      Conversion,
      .pred_class
    ),
    ROC_AUC = roc_auc_vec(
      Conversion,
      .pred_Yes,
      event_level = "second"
    ),
    Sensitivity = sens_vec(
      Conversion,
      .pred_class,
      event_level = "second"
    ),
    Specificity = spec_vec(
      Conversion,
      .pred_class,
      event_level = "second"
    ),
    .groups = "drop"
  )

ao4_metrics


# ROC curves
ao4_results |>
  group_by(model) |>
  roc_curve(
    Conversion,
    .pred_Yes,
    event_level = "second"
  ) |>
  autoplot() +
  labs(
    title = "ROC Curves — AO4 Classification Models"
  )
```

- **Regression:** Linear Regression is evaluated using RMSE, MAE, and R²
  to determine how well customer behavior predicts `ConversionRate`.

------------------------------------------------------------------------

- **Classification:** Logistic Regression, Decision Tree, and Random
  Forest are compared using the same held-out test set.
- Because approximately **87.7% of customers converted**, accuracy alone
  may overstate model performance.
- **ROC AUC is the primary classification metric**, because it measures
  how well each model distinguishes converters from non-converters
  across probability thresholds.

## AO4: Interpretation

```{r}
# Logistic Regression Odds Ratios
ao4_odds <- ao4_fit_logit |>
  extract_fit_parsnip() |>
  tidy(exponentiate = TRUE, conf.int = TRUE) |>
  filter(term != "(Intercept)") |>
  arrange(desc(estimate))

ao4_odds

# Random Forest Variable Importance
rf_engine <- ao4_fit_rf |>
  extract_fit_engine()

ao4_importance <- tibble(
  Variable = names(rf_engine$variable.importance),
  Importance = rf_engine$variable.importance
) |>
  arrange(desc(Importance))

ggplot(
  ao4_importance,
  aes(x = reorder(Variable, Importance),
      y = Importance)
) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "AO4 Random Forest Variable Importance",
    x = "Predictor",
    y = "Importance"
  ) +
  theme_minimal()
```

- **PreviousPurchases** is the strongest predictor, followed by
  **EmailOpens** and **EmailClicks**.
- Purchase history appears to be more useful for predicting conversion
  than email engagement alone.
- The model has **moderate predictive power (ROC AUC = 0.656)**, so the
  results should be interpreted with caution.

::: incremental
## AO4: Summary Findings

- Higher **EmailOpens, EmailClicks, and PreviousPurchases** are
  associated with higher conversion.

- **PreviousPurchases** is the strongest predictor, followed by
  **EmailOpens** and **EmailClicks**.

- Model performance is **moderate (ROC AUC = 0.656)**; the **87.6%
  conversion rate** also means accuracy alone can be misleading.

- **Business implication:** use both **purchase history and email
  engagement** to identify customers with higher conversion potential.
:::

<!-- =================================================================== -->

<!-- AO5 — Predictive Analytics  -->

<!-- =================================================================== -->

# Analytics Objective 5 — *Sora Hosoda*

```{r}
#| label: ao2-hidden-setup
#| include: false
#| warning: false
#| message: false

set.seed(2025)

ao2_data <- raw_data |>
  transmute(
    Age,
    Gender = factor(Gender),
    Income,
    CampaignChannel = factor(CampaignChannel),
    CampaignType = factor(CampaignType),
    AdSpend,
    ClickThroughRate,
    WebsiteVisits,
    PagesPerVisit,
    TimeOnSite,
    SocialShares,
    EmailOpens,
    EmailClicks,
    PreviousPurchases,
    LoyaltyPoints,
    Conversion = factor(
      Conversion,
      levels = c(1, 0),
      labels = c("Yes", "No")
    )
  )

set.seed(617)

ao2_split <- initial_split(
  ao2_data,
  prop = 0.80,
  strata = Conversion
)

ao2_train <- training(ao2_split)
ao2_test <- testing(ao2_split)

ao2_xgb_rec <- recipe(
  Conversion ~ .,
  data = ao2_train
) |>
  step_impute_median(all_numeric_predictors()) |>
  step_novel(all_nominal_predictors()) |>
  step_unknown(all_nominal_predictors()) |>
  step_dummy(all_nominal_predictors(), one_hot = TRUE) |>
  step_zv(all_predictors())

ao2_xgb_spec <- boost_tree(
  trees = 300,
  tree_depth = 6,
  learn_rate = 0.05,
  min_n = 30
) |>
  set_engine("xgboost") |>
  set_mode("classification")

ao2_xgb_wf <- workflow() |>
  add_recipe(ao2_xgb_rec) |>
  add_model(ao2_xgb_spec)

set.seed(2025)

ao2_xgb_fit <- fit(
  ao2_xgb_wf,
  data = ao2_train
)

ao2_xgb_prep <- prep(
  ao2_xgb_rec,
  training = ao2_train
)

ao2_xgb_baked <- bake(
  ao2_xgb_prep,
  new_data = ao2_train
)

ao2_predictor_names <- setdiff(
  names(ao2_xgb_baked),
  "Conversion"
)

ao2_xgb_matrix <- as.matrix(
  ao2_xgb_baked[, ao2_predictor_names]
)

ao2_xgb_engine <- workflows::extract_fit_parsnip(
  ao2_xgb_fit
)$fit
```

## AO5: Predictive Analytics

> **Research Objective:** To develop a predictive model that identifies
> the most useful factors for predicting customer conversion using
> customer demographics, campaign information, engagement variables, and
> purchase history.

- **Outcome:** `Conversion` (Yes / No)
- **Predictors:** 15 customer and marketing variables
- **Problem type:** Binary classification
- **Analytical focus:** Compare multiple classification models and
  identify the strongest predictors of conversion.

::: key-message
Which factors are most useful for predicting customer conversion when
all major predictor groups are considered together?
:::

::: notes
This objective combines customer demographics, campaign information,
engagement variables, and purchase history in one overall predictive
analysis.
:::

## AO5: Machine Learning Methods to be Used

::: panel-tabset
### Regression-Focused Methods

- Not used because `Conversion` is a binary outcome.
- The analysis focuses on classification models.

### Classification-Focused Methods

- **Logistic Regression** — interpretable baseline classification model
- **Decision Tree** — captures nonlinear decision rules and interactions

### Ensembles

- **Random Forest** — combines many decision trees
- **XGBoost** — sequentially builds trees to improve prediction
:::

::: takeaway
Four models were compared to determine whether ensemble methods improve
prediction over simpler classification models.
:::

## AO5: Data Wrangling & Visualization

::::: columns
::: {.column width="56%"}
```{r}
#| echo: false

ao2_predictor_groups <- tibble::tribble(
  ~Category, ~Variables,
  "Customer Profile", "Age, Gender, Income",
  "Campaign", "Channel, Type, Ad Spend",
  "Engagement", "CTR, Website Visits, Pages per Visit, Time on Site, Email Activity, Social Shares",
  "History", "Previous Purchases, Loyalty Points"
)

knitr::kable(
  ao2_predictor_groups,
  col.names = c("Predictor Group", "Variables")
)
```
:::

::: {.column width="40%"}
```{r}
#| echo: false

ao2_balance <- tibble::tribble(
  ~Conversion, ~Customers, ~Share,
  "Yes", "7,012", "87.6%",
  "No", "988", "12.4%"
)

knitr::kable(ao2_balance)
```

**Class imbalance:** About 88% of customers converted.
:::
:::::

::: takeaway
Because the outcome is highly imbalanced, ROC AUC was prioritized over
accuracy when comparing models.
:::

::: notes
The analysis uses 15 predictors from four broad categories. Conversion
is highly imbalanced, so accuracy alone can be misleading.
:::

## AO5: Model Fitting

::::: columns
::: {.column width="48%"}
### Data Splitting

- **80% training / 20% testing**
- Stratified by `Conversion`
- Test data held out for final evaluation

### Recipe Creation

- Median imputation
- Novel and unknown factor handling
- Dummy encoding
- Zero-variance removal
:::

::: {.column width="48%"}
### Model Specification

1.  Logistic Regression
2.  Decision Tree
3.  Random Forest
4.  XGBoost

### Model Selection

- **10-fold stratified cross-validation**
- Hyperparameter tuning for ensemble models
- Primary metric: **ROC AUC**
:::
:::::

::: key-message
The same training data and cross-validation framework were used to
compare model performance.
:::

::: notes
The data was split before model development. Cross-validation was
conducted within the training data, while the test set remained
untouched until final evaluation.
:::

## AO5: Prediction & Model Evaluation

::::: columns
::: {.column width="60%"}
```{r}
#| echo: false
#| fig-width: 7.5
#| fig-height: 4.6

ao2_cv <- tibble::tribble(
  ~Model, ~ROC_AUC,
  "XGBoost", 0.818,
  "Random Forest", 0.795,
  "Logistic Regression", 0.779,
  "Decision Tree", 0.699
)

ggplot(
  ao2_cv,
  aes(
    x = reorder(Model, ROC_AUC),
    y = ROC_AUC
  )
) +
  geom_col(fill = "#1f3864", width = 0.65) +
  geom_text(
    aes(label = sprintf("%.3f", ROC_AUC)),
    hjust = -0.15,
    size = 4.5
  ) +
  coord_flip() +
  scale_y_continuous(
    limits = c(0, 0.90),
    expand = expansion(mult = c(0, 0.02))
  ) +
  labs(
    title = "10-Fold Cross-Validation ROC AUC",
    x = NULL,
    y = "Mean ROC AUC"
  ) +
  theme_minimal(base_size = 13)
```
:::

::: {.column width="36%"}
### Best Model: XGBoost

| Metric      | Test Result |
|-------------|------------:|
| ROC AUC     |   **0.844** |
| Accuracy    |   **91.8%** |
| Sensitivity |   **99.5%** |
| Specificity |   **37.4%** |

**Confusion Matrix**

|               | Actual Yes | Actual No |
|---------------|-----------:|----------:|
| Predicted Yes |  **1,396** |       124 |
| Predicted No  |          7 |    **74** |
:::
:::::

::: takeaway
XGBoost achieved the highest cross-validation ROC AUC and the strongest
overall test performance.
:::

::: notes
XGBoost had the highest cross-validation ROC AUC at 0.818. On the test
set, ROC AUC increased to 0.844. Sensitivity was very high, although
non-converters remained more difficult to identify.
:::

## AO5: Interpretation — Variable Importance & SHAP

::::: columns
::: {.column width="48%"}
```{r}
#| echo: false
#| fig-width: 6.6
#| fig-height: 4.5

ao2_vip_plot <- ao2_xgb_fit |>
  workflows::extract_fit_parsnip() |>
  vip::vip(
    num_features = 10
  ) +
  labs(
    title = "XGBoost Variable Importance",
    x = "Importance",
    y = NULL
  ) +
  theme_minimal(base_size = 11)

print(ao2_vip_plot)
```
:::

::: {.column width="48%"}
```{r}
#| echo: false
#| fig-width: 6.6
#| fig-height: 4.5

ao2_shap_values <- predict(
  ao2_xgb_engine,
  ao2_xgb_matrix,
  predcontrib = TRUE
)

ao2_shap_matrix <- as.matrix(
  ao2_shap_values
)

ao2_shap_matrix <- ao2_shap_matrix[
  ,
  !colnames(ao2_shap_matrix) %in% c("BIAS", "(Intercept)"),
  drop = FALSE
]

ao2_shap_importance <- data.frame(
  Feature = colnames(ao2_shap_matrix),
  Mean_Abs_SHAP = colMeans(abs(ao2_shap_matrix))
) |>
  arrange(desc(Mean_Abs_SHAP)) |>
  slice_head(n = 10)

ggplot(
  ao2_shap_importance,
  aes(
    x = reorder(Feature, Mean_Abs_SHAP),
    y = Mean_Abs_SHAP
  )
) +
  geom_col(fill = "#2e75b6", width = 0.65) +
  coord_flip() +
  labs(
    title = "SHAP Feature Importance",
    x = NULL,
    y = "Mean Absolute SHAP"
  ) +
  theme_minimal(base_size = 10.5)
```
:::
:::::

::: takeaway
SHAP identified `CampaignType_Conversion`, EmailClicks,
PreviousPurchases, ClickThroughRate, LoyaltyPoints, and PagesPerVisit as
leading contributors to prediction.
:::

::: notes
Variable importance and SHAP provide complementary views of the fitted
XGBoost model. The interpretation indicates that campaign, engagement,
and customer-history information contributed strongly to prediction.
:::

## AO5: Interpretation — Partial Dependence Plot

```{r}
#| echo: false
#| fig-width: 9
#| fig-height: 4.8

ao2_adspend_values <- seq(
  from = quantile(ao2_train$AdSpend, 0.05),
  to = quantile(ao2_train$AdSpend, 0.95),
  length.out = 30
)

ao2_pdp_list <- lapply(
  ao2_adspend_values,
  function(value) {

    temp_data <- ao2_train
    temp_data$AdSpend <- value

    temp_baked <- bake(
      ao2_xgb_prep,
      new_data = temp_data
    )

    temp_matrix <- as.matrix(
      temp_baked[, ao2_predictor_names]
    )

    temp_prediction <- predict(
      ao2_xgb_engine,
      xgboost::xgb.DMatrix(temp_matrix)
    )

    data.frame(
      AdSpend = value,
      Predicted_Conversion = mean(temp_prediction)
    )
  }
)

ao2_pdp <- bind_rows(ao2_pdp_list)

ggplot(
  ao2_pdp,
  aes(
    x = AdSpend,
    y = Predicted_Conversion
  )
) +
  geom_line(
    linewidth = 1.2,
    color = "#1f3864"
  ) +
  labs(
    title = "Partial Dependence of Conversion on Ad Spend",
    x = "Ad Spend",
    y = "Average Predicted Conversion Probability"
  ) +
  theme_minimal(base_size = 13)
```

::: takeaway
Predicted conversion remained fairly stable at lower spending levels,
increased around **Ad Spend ≈ 5,000**, and then remained relatively
high.
:::

::: notes
The PDP describes the relationship learned by the model. It should not
be interpreted as evidence that increasing ad spend directly causes
conversion.
:::

## AO5: Summary Findings

::::: columns
::: {.column width="48%"}
### Model Findings

- **XGBoost** was the strongest model.
- CV ROC AUC = **0.818**
- Test ROC AUC = **0.844**
- Very high sensitivity = **99.5%**
- Non-converters remained harder to identify.
:::

::: {.column width="48%"}
### Interpretation

- Campaign type contributed strongly.
- Email engagement was important.
- Previous purchases and loyalty contributed.
- Website engagement also mattered.
- Demographics contributed less.
:::
:::::

::: key-message
**Customer actions, campaign context, and purchase history were more
useful for predicting conversion than demographic characteristics
alone.**
:::

::: notes
Overall, XGBoost provided the strongest predictive performance. The
interpretation results indicate that campaign context, engagement, and
previous customer behavior were more useful than demographics for
predicting conversion.
:::

# Conclusion

## Key Findings

- **Campaign type mattered more than channel:** Conversion-focused
  campaigns had the highest conversion rates.
- **Customer behavior was useful for prediction:** Engagement, previous
  purchases, loyalty, and website activity contributed to conversion
  prediction.
- **Demographics had limited predictive value:** Age, gender, and income
  were weaker predictors.
- **XGBoost performed best:** CV ROC AUC = **0.818** and test ROC AUC =
  **0.844**.
- **Class imbalance mattered:** About **88%** of customers converted, so
  accuracy alone was not sufficient.

## Recommendations for Businesses

- **Focus on customer behavior:** Use engagement and purchase history to
  support customer targeting.
- **Consider campaign type:** Conversion-focused campaigns showed
  stronger conversion results.
- **Do not rely on channel alone:** Also consider cost, reach, and
  audience fit.
- **Use predictive models for targeting:** XGBoost can combine multiple
  customer and campaign factors.
- **Evaluate models beyond accuracy:** Consider ROC AUC, sensitivity,
  and specificity.

## Limitations and Directions for Future Research

- **`Conversion` is not clearly defined:** The dataset does not specify
  what customer action counts as a conversion.
- **The outcome is imbalanced:** Non-converters were more difficult to
  identify.
- **Time and location are not provided:** The dataset does not specify a
  campaign period or geographic region.
- **The results are not causal:** The analysis identifies associations
  and predictive patterns.
- **The findings come from one dataset:** Future research should test
  other datasets and customer populations.
- **Future research should clearly define conversion** and explore ways
  to improve prediction of non-converters.

## Appendix

- **GitHub Repo:** <https://github.com/gracesen/IBM6540-Group3>
- **GitHub Pages:** <https://gracesen.github.io/IBM6540-Group3/>
- **Presentation Slides:**
  <https://gracesen.github.io/IBM6540-Group3/final_report_presentation_2.html>

## Thank You / Q&A
